---
title: "Ifatico Pain"
author: "JR"
date: "2024-07-29"
output: html_document
---

load packages
```{r message=FALSE, warning=FALSE}
library(compareGroups)
library(PairedData)
library(readxl)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(Rmisc) 
library(readxl)
library(ggpubr) 
library(rstatix) 
library(WRS2)
library(dplyr) 
library(effectsize)
library(dplyr)
library(MOTE)
library(colorspace)
library(readr)
```


Load data
```{r}
all_data <- readRDS(file = "all_data.rds")
```

Varianzanalyse FATIGUE und MECFS
```{r}
table(all_data$f_group)
```


########################################### PDT

Create plot
```{r}
bp_fatigue_pdt <- ggviolin(all_data, x = "f_group", y = "qst_cuff_1_pdt",
   fill = "f_group",
   palette = c("#00AFBB","deeppink","purple"),
   color = "f_group",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "PDT values for MECFS moderate/ severe and healhy controls",
  xlab = c("Group"),
  ylab = c("PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Moderate","Severe")) + rremove("legend")

bp_fatigue_pdt_final <- ggpar(bp_fatigue_pdt, ylim = c(0,100))
#pdt_plot_final
add_summary(bp_fatigue_pdt_final, "mean", color = "black",size = 0.5)
```
Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(f_group) %>%
  rstatix::shapiro_test(qst_cuff_1_pdt)
all_data %>%
  group_by(f_group) %>%
  identify_outliers(qst_cuff_1_pdt) %>% select(id,f_group,qst_cuff_1_pdt,is.outlier,is.extreme)

```
--> no extreme outlier
--> Severe data not normal distributed

Test for equal variances
```{r}
aov_fatigue_pdt_var <- if(all_data %>% 
rstatix::levene_test(qst_cuff_1_pdt ~ f_group) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>% 
rstatix::levene_test(qst_cuff_1_pdt ~ f_group)
```
Equal variances

Anova and Kruskal test
```{r}
aov_fatigue_pdt <- anova_test(qst_cuff_1_pdt ~ f_group, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_pdt, correction = "auto")
rstatix::kruskal_test(qst_cuff_1_pdt ~ f_group, data = all_data)
```
--> both significant 



T-test and Wilcox test
```{r}
all_data  %>% rstatix::t_test(
         qst_cuff_1_pdt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_fatigue_pdt_var)
all_data  %>% rstatix::wilcox_test(
         qst_cuff_1_pdt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```
Different results:
Wilcox Test:
HC vs Severe significant

T test:
--> 	HC vs. Moderate significant
--> 	HC vs. Severe significant


Get effectsize and bootrstrapped ci
```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  qst_cuff_1_pdt ~ f_group,
  comparisons = NULL,
  ref.group = "HC",
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```




###########################   PTT

Create plot
```{r}
bp_fatigue_ptt <- ggviolin(all_data, x = "f_group", y = "qst_cuff_1_ptt",
   fill = "f_group",
   palette = c("#00AFBB","deeppink","purple"),
   color = "f_group",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "PTT values for MECFS moderate/ severe and healhy controls",
  xlab = c("Group"),
  ylab = c("PTT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Moderate","Severe")) + rremove("legend")

bp_fatigue_ptt_final <- ggpar(bp_fatigue_ptt, ylim = c(0,100))
#ptt_plot_final
add_summary(bp_fatigue_ptt_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(f_group) %>%
  rstatix::shapiro_test(qst_cuff_1_ptt)

all_data %>%
  group_by(f_group) %>%
  identify_outliers(qst_cuff_1_ptt)
```
--> Hc and severe not normal distributed
--> no outlier


Test for equal variances
```{r}
aov_fatigue_ptt_var <-  if(all_data %>%
rstatix::levene_test(qst_cuff_1_ptt ~ f_group) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
rstatix::levene_test(qst_cuff_1_ptt ~ f_group)
```
--> var are equal



```{r}
aov_fatigue_ptt <- anova_test(qst_cuff_1_ptt ~ f_group, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_ptt, correction = "auto")
rstatix::kruskal_test(qst_cuff_1_ptt ~ f_group, data = all_data)
```
--> Both anova and kurskal test are significant

T-test and Wilcox test
```{r}
all_data  %>% rstatix::t_test(
         qst_cuff_1_ptt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", var.equal = aov_fatigue_ptt_var)
all_data  %>% rstatix::wilcox_test(
         qst_cuff_1_ptt ~ f_group, paired = FALSE, 
         p.adjust.method = "none")
```

--> Moderate and Severe and sig. different to HC
--> No sig diff between HC Moderate and severe (both tests)  

Get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  qst_cuff_1_ptt ~ f_group,
  comparisons = NULL,
  ref.group = "HC",
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```


################ SSP PDT ################

Create Plot
```{r}
bp_fatigue_ssp_pdt <- ggviolin(all_data, x = "f_group", y = "ssp_ratio_pdt",
   fill = "f_group",
   palette = c("#00AFBB","deeppink","purple"),
   color = "f_group",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "SSP PDT values for MECFS moderate/ severe and healhy controls",
  xlab = c("Group"),
  ylab = c("SSP PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Moderate","Severe")) + rremove("legend")

bp_fatigue_ssp_pdt_final <- ggpar(bp_fatigue_ssp_pdt, ylim = c(0,3))
#pdt_plot_final
add_summary(bp_fatigue_ssp_pdt_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(f_group) %>%
  rstatix::shapiro_test(ssp_ratio_pdt)

all_data %>%
  group_by(f_group) %>%
  identify_outliers(ssp_ratio_pdt) %>% select(id,f_group,ssp_ratio_pdt,is.outlier,is.extreme)
```
--> Hc and Moderate data are not normal distributed
-->Two extreme outlier


test for equal variances
```{r}
all_data %>%
rstatix::levene_test(ssp_ratio_pdt ~ f_group)
```
--> var are equal

Anova and kurskal test
```{r}
aov_fatigue_ssp_pdt <- anova_test(ssp_ratio_pdt ~ f_group, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_ssp_pdt, correction = "auto")
rstatix::kruskal_test(ssp_ratio_pdt ~ f_group, data = all_data)
```
--> kruskal test and anova both not significant

Sensitivity analyis
```{r}
fatigue_ssp_pdt_out_id <- all_data %>% group_by(f_group) %>% identify_outliers(ssp_ratio_pdt) %>% 
                                       filter(is.extreme == TRUE) %>% pull(id)
  
aov_fatigue_ssp_pdt_out <- all_data %>% filter(!id %in% fatigue_ssp_pdt_out_id) %>% anova_test(ssp_ratio_pdt ~ f_group, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_ssp_pdt_out, correction = "auto")
all_data %>% filter(!id %in% fatigue_ssp_pdt_out_id) %>% rstatix::kruskal_test(ssp_ratio_pdt ~ f_group)
```
Sensitivity analysis: No diff. Still both test not significant



###############################   SSP PTT

Create Plot
```{r}
bp_fatigue_ssp_ptt <- ggviolin(all_data, x = "f_group", y = "ssp_ratio_ptt",
   fill = "f_group",
   palette = c("#00AFBB","deeppink","purple"),
   color = "f_group",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "SSP PTT values for MECFS moderate/ severe and healhy controls",
  xlab = c("Group"),
  ylab = c("SSP PTT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Moderate","Severe")) + rremove("legend")

bp_fatigue_ssp_ptt_final <- ggpar(bp_fatigue_ssp_ptt, ylim = c(0,3))
#ptt_plot_final
add_summary(bp_fatigue_ssp_ptt_final, "mean", color = "black",size = 0.5)
```


Search for extreme outlier and test for normal distribution
```{r}
 all_data %>%
  dplyr::group_by(f_group) %>%
  rstatix::shapiro_test(ssp_ratio_ptt)

all_data %>%
  group_by(f_group) %>%
  identify_outliers(ssp_ratio_ptt) %>% select(id,f_group,ssp_ratio_ptt,is.outlier,is.extreme)
```
--> only severe data normal distributed
--> 2 extreme outlier

```{r}
aov_fatigue_ssp_ptt_var <- if(all_data %>%
rstatix::levene_test(ssp_ratio_ptt ~ f_group) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
rstatix::levene_test(ssp_ratio_ptt ~ f_group)
```
--> var are equal


Anova and kurskal test
```{r}
aov_fatigue_ssp_ptt <- anova_test(ssp_ratio_ptt ~ f_group, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_ssp_ptt, correction = "auto")
rstatix::kruskal_test(ssp_ratio_ptt ~ f_group, data = all_data)
```
Anova is not sig but Kruskal-Wallis test is

T-test and wilcox test
```{r}
all_data  %>% rstatix::t_test(
         ssp_ratio_ptt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", var.equal = aov_fatigue_ssp_ptt_var)
all_data  %>% rstatix::wilcox_test(
         ssp_ratio_ptt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

--> wilcox test: sig dif between HC and Severe
--> t test: sig diff between Moderate and severe


Sensitivity analysis
```{r}
fatigue_ssp_ptt_out_id <- all_data %>% group_by(f_group) %>% identify_outliers(ssp_ratio_ptt) %>%
                                       filter(is.extreme == TRUE) %>% pull(id)
  
  
aov_fatigue_ssp_ptt_out <- all_data %>% filter(!id %in% fatigue_ssp_ptt_out_id) %>% anova_test(ssp_ratio_ptt ~ f_group, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_ssp_ptt_out, correction = "auto")
all_data %>% filter(!id %in% fatigue_ssp_ptt_out_id) %>% rstatix::kruskal_test(ssp_ratio_ptt ~ f_group)
```
--> sensitivity analysis: now both are sig.

T-test and wilcox test (sensitivity analysis)
```{r}
all_data %>% filter(!id %in% fatigue_ssp_ptt_out_id) %>% rstatix::t_test(
         ssp_ratio_ptt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_fatigue_ssp_ptt_var)
all_data %>% filter(!id %in% fatigue_ssp_ptt_out_id) %>% rstatix::wilcox_test(
         ssp_ratio_ptt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

Sensitivity analyis: t test and wilcox test: Hc vs severe sig. differences

Get effect size and bootstrapped ci 
```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  ssp_ratio_ptt ~ f_group,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

Get effect size and bootstrapped ci (sensitivity analysis)
```{r}
set.seed(777)
all_data %>% filter(!id %in% fatigue_ssp_ptt_out_id)  %>% rstatix::cohens_d(
  ssp_ratio_ptt ~ f_group,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```



########################  CPM PDT 

Create plot
```{r}
bp_fatigue_cpm_pdt <- ggviolin(all_data, x = "f_group", y = "cpm_dif_pdt",
   fill = "f_group",
   palette = c("#00AFBB","deeppink","purple"),
   color = "f_group",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = " CPM PDT values for MECFS moderate/ severe and healhy controls",
  xlab = c("Group"),
  ylab = c("CPM PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Moderate","Severe")) + rremove("legend")

bp_fatigue_cpm_pdt_final <- ggpar(bp_fatigue_cpm_pdt, ylim = c(-25,50))
#pdt_plot_final
add_summary(bp_fatigue_cpm_pdt_final, "mean", color = "black",size = 0.5)
```

Serach for extreme outlier and test for normal distribution
```{r}
 all_data %>%
  dplyr::group_by(f_group) %>%
  rstatix::shapiro_test(cpm_dif_pdt)

all_data %>%
  group_by(f_group) %>%
  identify_outliers(cpm_dif_pdt) %>% select(id,f_group,cpm_dif_pdt,is.outlier,is.extreme)


```
--> severe data are not normal distributed
--> no extreme outlier


Test for equal variances
```{r}
aov_fatigue_cpm_pdt_var <- if(all_data %>%
rstatix::levene_test(cpm_dif_pdt ~ f_group) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
rstatix::levene_test(cpm_dif_pdt ~ f_group)
```
--> var are equal

Anova and Kurskal Test
```{r}
aov_fatigue_cpm_pdt <- anova_test(cpm_dif_pdt ~ f_group, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_cpm_pdt, correction = "auto")
rstatix::kruskal_test(cpm_dif_pdt ~ f_group, data = all_data)
```

-->	Kruskal-Wallis is sig but anova is not



T-test and wilcox test
```{r}
all_data  %>% rstatix::t_test(
         cpm_dif_pdt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_fatigue_cpm_pdt_var)
all_data  %>% rstatix::wilcox_test(
         cpm_dif_pdt ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

--> t-test and wilcox test: sig for 	HC vs	Moderate


```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  cpm_dif_pdt ~ f_group,
  comparisons = NULL,
  ref.group = "HC",
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```






##########################   CPM PTT

Create for plot 
```{r}
bp_fatigue_cpm_ptt <- ggviolin(all_data, x = "f_group", y = "cpm_dif_ptt",
   fill = "f_group",
   palette = c("#00AFBB","deeppink","purple"),
   color = "f_group",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = " CPM PTT values for MECFS moderate/ severe and healhy controls",
  xlab = c("Group"),
  ylab = c("CPM PTT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Moderate","Severe")) + rremove("legend")

bp_fatigue_cpm_ptt_final <- ggpar(bp_fatigue_cpm_ptt, ylim = c(-25,50))
#ptt_plot_final
add_summary(bp_fatigue_cpm_ptt_final, "mean", color = "black",size = 0.5)
```


Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(f_group) %>%
  rstatix::shapiro_test(cpm_dif_ptt)

all_data %>%
  group_by(f_group) %>%
  identify_outliers(cpm_dif_ptt) %>% select(id,f_group,cpm_dif_pdt,is.outlier,is.extreme)
```
--> HC data not normal distributed
--> no extreme outlier

Test for equal variances
```{r}
all_data %>%
rstatix::levene_test(cpm_dif_ptt ~ f_group)
```
--> var are equal

Anova and kurskal test
```{r}
aov_fatigue_cpm_ptt <- anova_test(cpm_dif_ptt ~ f_group, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_cpm_ptt, correction = "auto")
rstatix::kruskal_test(cpm_dif_ptt ~ f_group, data = all_data)
```

Both not significant



######################   TSP 

Create long_df to plot line graph
```{r}
tsp_line_long <- all_data %>% select(id,gruppe,pain,f_group,mecfs,qst_temporal_1:qst_temporal_10) %>% pivot_longer(cols = qst_temporal_1:qst_temporal_10,names_to = "timepoint",values_to = "VAS.Rating") %>% mutate(timepoint = sub("qst_temporal_","",timepoint))
```



Create line plot
```{r}
tsp_line_plot3 <- ggline(tsp_line_long, x = "timepoint", y = "VAS.Rating", color = "f_group",
 add = "mean_se", palette = c("#00AFBB","deeppink","purple")) 

tsp_line_plot3 <- ggpar(tsp_line_plot3, ylim = c(0,10))
tsp_line_plot3
```


Create plot
```{r}
bp_tsp_fatigue <- ggviolin(all_data, x = "f_group", y = "tsp",
   fill = "f_group",
   palette = c("#00AFBB","deeppink","purple"),
   color = "f_group",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "TSP values for MECFS moderate/ severe and healhy controls",
  xlab = c("Group"),
  ylab = c("TSP"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Moderate","Severe")) + rremove("legend")

bp_tsp_fatigue_final <- ggpar(bp_tsp_fatigue, ylim = c(-10,10))
#pdt_plot_final
add_summary(bp_tsp_fatigue_final, "mean", color = "black",size = 0.5)
```
Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(f_group) %>%
  rstatix::shapiro_test(tsp)

all_data %>%
  group_by(f_group) %>%
  identify_outliers(tsp) %>% select(id,f_group,tsp,is.outlier,is.extreme)

```
--> Severe data not normal distributed
--> One extreme outlier

Test for equal variances
```{r}
aov_fatigue_tsp_var <- if(all_data %>%
rstatix::levene_test(tsp ~ f_group) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
rstatix::levene_test(tsp ~ f_group)
```
--> var are equal

Anova and Kruskal test
```{r}
aov_fatigue_tsp <- anova_test(tsp ~ f_group, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_tsp, correction = "auto")
rstatix::kruskal_test(tsp ~ f_group, data = all_data)
```
--> anova is significant but kruskal  is not 

Sensitivity analysis
```{r}
fatigue_tsp_out_id <- all_data %>% group_by(f_group) %>% identify_outliers(tsp) %>% 
                                   filter(is.extreme == TRUE) %>% pull(id)
aov_fatigue_tsp_out <- all_data  %>% filter(!id %in% fatigue_tsp_out_id) %>%
anova_test(tsp ~ f_group, detailed = TRUE)
rstatix::get_anova_table(aov_fatigue_tsp_out, correction = "auto")
all_data %>% filter(!id %in% fatigue_tsp_out_id) %>%rstatix::kruskal_test(tsp ~ f_group)
```
No dif.: ANova is sig but Kruskal  is not sig

T-test and wilcox test
```{r}
all_data %>% rstatix::t_test(
         tsp ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_fatigue_tsp_var)
all_data %>% rstatix::wilcox_test(
         tsp ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```
 t test: sig results for HC	vs Moderate
 wilcox test: no sig results


T-test and wilcox test (sensitivity analysis)
```{r}
all_data %>% filter(!id %in% fatigue_tsp_out_id) %>% rstatix::t_test(
         tsp ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_fatigue_tsp_var)
all_data %>% filter(!id %in% fatigue_tsp_out_id) %>% rstatix::wilcox_test(
         tsp ~ f_group, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```
 t test: sig results for HC	vs Moderate
 wilcox test: no sig results

Sensitivity analysis: no differences

Get effect size and bootstrapped ci 
```{r}
set.seed(777)
all_data %>% filter(f_group != "Severe") %>% mutate(f_group = droplevels(f_group)) %>% rstatix::cohens_d(
  tsp ~ f_group,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

Get effect size and bootstrapped ci (sensitivity analysis)
```{r}
set.seed(777)
all_data %>% filter(!id %in% fatigue_tsp_out_id) %>% filter(f_group != "Severe") %>% mutate(f_group = droplevels(f_group))  %>% rstatix::cohens_d(
  tsp ~ f_group,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```














