---
title: "Ifatico Pain"
author: "JR"
date: "2024-07-29"
output: html_document
---

load packages
```{r message=FALSE, warning=FALSE}
library(compareGroups)
library(PairedData)
library(readxl)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(Rmisc) 
library(readxl)
library(ggpubr) 
library(rstatix) 
library(WRS2)
library(dplyr) 
library(effectsize)
library(dplyr)
library(MOTE)
library(colorspace)
library(readr)
```


Load data
```{r}
all_data <- readRDS(file = "all_data.rds")
```

```{r}
table(all_data$pain)
```
############  PDT

Create plot
```{r}
bp_sub_pdt <- ggviolin(all_data, x = "pain", y = "qst_cuff_1_pdt",
   fill = "pain",
   palette = c("#00AFBB","#FC4E07","red"),
   color = "pain",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "PDT values for post-covid patients and healthy controls",
  xlab = c("Group"),
  ylab = c("PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_pain","Cov_pain")) + rremove("legend")

bp_sub_pdt_final <- ggpar(bp_sub_pdt, ylim = c(0,100))
#pdt_plot_final
add_summary(bp_sub_pdt_final, "mean", color = "black",size = 0.5)
```

Search for extreme ourlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(pain) %>%
  rstatix::shapiro_test(qst_cuff_1_pdt)
all_data %>%
  group_by(pain) %>%
  identify_outliers(qst_cuff_1_pdt) %>% dplyr::select(id,pain,qst_cuff_1_pdt,is.outlier,is.extreme)

```
--> Cov_pain not normal distributed
--> No extreme outlier

Test for equal variances
```{r}
sub_pdt_variance <- if(all_data %>% 
rstatix::levene_test(qst_cuff_1_pdt ~ pain) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>% 
rstatix::levene_test(qst_cuff_1_pdt ~ pain)
```

T-test and wilcox test
```{r}
all_data %>% rstatix::t_test(
         qst_cuff_1_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_pdt_variance)
all_data %>% rstatix::wilcox_test(
         qst_cuff_1_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```
--> only HC vs Cov_pain significant (t-test and wilcox-test)

get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data %>% dplyr::filter(pain != "Cov_no_pain") %>% mutate(pain = droplevels(pain)) %>%rstatix::cohens_d(
  qst_cuff_1_pdt ~ pain,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = sub_pdt_variance,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

##############################  PTT

Create plot
```{r}
bp_sub_ptt <- ggviolin(all_data, x = "pain", y = "qst_cuff_1_ptt",
   fill = "pain",
   palette = c("#00AFBB","#FC4E07","red"),
   color = "pain",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "PTT values for post-covid patients and healthy controls",
  xlab = c("Group"),
  ylab = c("PTT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_pain","Cov_pain")) + rremove("legend")

bp_sub_ptt_final <- ggpar(bp_sub_ptt, ylim = c(0,100))
#ptt_plot_final
add_summary(bp_sub_ptt_final, "mean", color = "black",size = 0.5)
```

Search for extreme otliers and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(pain) %>%
  rstatix::shapiro_test(qst_cuff_1_ptt)

all_data %>%
  group_by(pain) %>%
  identify_outliers(qst_cuff_1_ptt) %>% select(id,pain,qst_cuff_1_ptt,is.outlier,is.extreme)
```
--> Cov_pain and HC data are not normal distributed
--> no extreme outlier

Test for equal variances
```{r}
sub_ptt_variance <- if(all_data  %>%
rstatix::levene_test(qst_cuff_1_ptt ~ pain) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data  %>%
rstatix::levene_test(qst_cuff_1_ptt ~ pain)
```


T-test and wilcox test
```{r}
all_data  %>% rstatix::t_test(
         qst_cuff_1_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_ptt_variance)
all_data  %>% rstatix::wilcox_test(
         qst_cuff_1_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```
Only cov_pain vs HC significant (for both Wilcox and t-test)

Get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data %>% filter(pain != "Cov_no_pain") %>% mutate(pain = droplevels(pain)) %>% rstatix::cohens_d(
  qst_cuff_1_ptt ~ pain,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = sub_ptt_variance,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

############################################TSP

Create long df to plot
```{r}
tsp_line_long <- all_data %>% select(id,gruppe,pain,f_group,mecfs,qst_temporal_1:qst_temporal_10) %>% pivot_longer(cols = qst_temporal_1:qst_temporal_10,names_to = "timepoint",values_to = "VAS.Rating") %>% mutate(timepoint = sub("qst_temporal_","",timepoint))
```

Create line plot
```{r}
tsp_line_plot2 <- ggline(tsp_line_long, x = "timepoint", y = "VAS.Rating", color = "pain",
 add = "mean_se", palette = c("#FC4E07","red","#00AFBB")) 

tsp_line_plot2 <- ggpar(tsp_line_plot2, ylim = c(0,10))
tsp_line_plot2
```

Create boxplot
```{r}
bp_tsp_sub <- ggviolin(all_data, x = "pain", y = "tsp",
   fill = "pain",
   palette = c("#00AFBB","#FC4E07","red"),
   color = "pain",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "TSP Dif values for post-covid patients and healthy controls",
  xlab = c("Group"),
  ylab = c("TSP"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_pain","Cov_pain")) + rremove("legend")

bp_tsp_sub_final <- ggpar(bp_tsp_sub, ylim = c(-10,10))
#pdt_plot_final
add_summary(bp_tsp_sub_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(pain) %>%
  rstatix::shapiro_test(tsp)

all_data %>%
  group_by(pain) %>%
  identify_outliers(tsp) %>% select(id,pain,tsp,is.outlier,is.extreme)
```
--> All covid data not normal distributed
--> 2 extreme outlier

Test for equal variances
```{r}
sub_tsp_variance <- if(all_data  %>%
rstatix::levene_test(tsp ~ pain) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data  %>%
rstatix::levene_test(tsp ~ pain)
```



T-test and wilcox test
```{r}
all_data %>%  rstatix::t_test(
         tsp ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_tsp_variance)
all_data %>% rstatix::wilcox_test(
         tsp ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```

Cov Pain sig difference to HC for t-test. Everying else not sig

```{r}
sub_tsp_out_id <- all_data %>% group_by(pain) %>% identify_outliers(tsp) %>%
                               filter(is.extreme == TRUE) %>% pull(id)
all_data %>% filter(!id %in% sub_tsp_out_id)  %>% rstatix::t_test(
         tsp ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_tsp_variance)
all_data %>% filter(!id %in% sub_tsp_out_id) %>% rstatix::wilcox_test(
         tsp ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```
-> Sensitivity analysis: same result

Outlier are in th cov_no_pain group --> no exclusion for es needed

Get effect size and bootrapped ci
```{r}
set.seed(777)
all_data  %>% filter(pain != "Cov_no_pain") %>% mutate(pain = droplevels(pain)) %>% rstatix::cohens_d(
  tsp ~ pain,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = sub_tsp_variance,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```



#########################   SSP PDT

Create plot
```{r}
bp_ssp_pdt_sub <- ggviolin(all_data, x = "pain", y = "ssp_ratio_pdt",
   fill = "pain",
   palette = c("#00AFBB","#FC4E07","red"),
   color = "pain",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "SSP PDT values for post-covid patients and healthy controls",
  xlab = c("Group"),
  ylab = c("SSP PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_pain","Cov_pain")) + rremove("legend")

bp_ssp_pdt_sub_final <- ggpar(bp_ssp_pdt_sub, ylim = c(0,3))
#pdt_plot_final
add_summary(bp_ssp_pdt_sub_final, "mean", color = "black",size = 0.5)
```



Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(pain) %>%
  rstatix::shapiro_test(ssp_ratio_pdt)

all_data %>%
  group_by(pain) %>%
  identify_outliers(ssp_ratio_pdt) %>% select(id,pain,ssp_ratio_pdt,is.outlier,is.extreme)

```
--> Cov_pain and HC data not normal distributed 
--> 2 extreme outlier

Test for equal variances
```{r}
sub_ssp_pdt_variance <- if(all_data  %>%
rstatix::levene_test(ssp_ratio_pdt ~ pain) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data  %>%
rstatix::levene_test(ssp_ratio_pdt ~ pain) 
```

T-test and wilcox test
```{r}
all_data %>% rstatix::t_test(
         ssp_ratio_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_ssp_pdt_variance)
all_data %>% rstatix::wilcox_test(
         ssp_ratio_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```
no significant differences for all tests

Sensitivity analysis
```{r}
sub_ssp_ratio_pdt_id <- all_data %>%
  group_by(pain) %>%
  identify_outliers(ssp_ratio_pdt) %>% filter(is.extreme == TRUE) %>% pull(id)

all_data %>% filter(!id %in% sub_ssp_ratio_pdt_id) %>% rstatix::t_test(
         ssp_ratio_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_ssp_pdt_variance)
all_data %>% filter(!id %in% sub_ssp_ratio_pdt_id) %>% rstatix::wilcox_test(
         ssp_ratio_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```
--> Sensitivity analysis: no dif


########################   SSP PTT

Create plot
```{r}
bp_ssp_ptt_sub <- ggviolin(all_data, x = "pain", y = "ssp_ratio_ptt",
   fill = "pain",
   palette = c("#00AFBB","#FC4E07","red"),
   color = "pain",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "SSP ptt values for post-covid patients and healthy controls",
  xlab = c("Group"),
  ylab = c("SSP ptt"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_pain","Cov_pain")) + rremove("legend")

bp_ssp_ptt_sub_final <- ggpar(bp_ssp_ptt_sub, ylim = c(0,3))
#ptt_plot_final
add_summary(bp_ssp_ptt_sub_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
 all_data %>%
  dplyr::group_by(pain) %>%
  rstatix::shapiro_test(ssp_ratio_ptt)

all_data %>%
  group_by(pain) %>%
  identify_outliers(ssp_ratio_ptt) %>% select(id,pain,ssp_ratio_ptt,is.outlier,is.extreme)
```
--> Cov_pain and HC data not normal distributed 
--> 2 extreme outlier

Test for equal variances
```{r}
sub_ssp_ptt_variance <- if(all_data %>%
rstatix::levene_test(ssp_ratio_ptt ~ pain) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data  %>%
rstatix::levene_test(ssp_ratio_ptt ~ pain)
```


T-Test and Wilcox-test
```{r}
all_data %>% rstatix::t_test(
         ssp_ratio_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_ssp_ptt_variance)

all_data %>% rstatix::wilcox_test(
         ssp_ratio_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```

--> T-test: no sig dif between Cov_pain and HC
--> Wilcox test: sig dif between Cov_pain and HC


Sensitivty analysis
```{r}
sub_ssp_ratio_ptt_id <- all_data %>%
  group_by(pain) %>%
  identify_outliers(ssp_ratio_ptt) %>% filter(is.extreme == TRUE) %>% pull(id)

all_data %>% filter(!id %in% sub_ssp_ratio_ptt_id) %>% rstatix::t_test(
         ssp_ratio_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_ssp_ptt_variance)
all_data %>% filter(!id %in% sub_ssp_ratio_ptt_id) %>% rstatix::wilcox_test(
         ssp_ratio_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```
--> sensitivity analyis sig dif between Cov_pain and HC for both (wilcox and t-test)


Get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data %>% filter(pain != "Cov_no_pain") %>% mutate(pain = droplevels(pain)) %>% rstatix::cohens_d(
  ssp_ratio_ptt ~ pain,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = sub_ssp_ptt_variance,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

Get effect size and bootstrapped ci (sensitivity analysis)
```{r}
set.seed(777)
all_data %>% filter(pain != "Cov_no_pain") %>% filter(!id %in% sub_ssp_ratio_ptt_id) %>% mutate(pain = droplevels(pain)) %>% rstatix::cohens_d(
  ssp_ratio_ptt ~ pain,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = sub_ssp_ptt_variance,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

#######################################  CPM PDT 

Create plot
```{r}
bp_cpm_pdt_sub <- ggviolin(all_data, x = "pain", y = "cpm_dif_pdt",
   fill = "pain",
   palette = c("#00AFBB","#FC4E07","red"),
   color = "pain",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "CPM PDT values for post-covid patients and healthy controls",
  xlab = c("Group"),
  ylab = c("CPM PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_pain","Cov_pain")) + rremove("legend")

bp_cpm_pdt_sub_final <- ggpar(bp_cpm_pdt_sub, ylim = c(-30,100))
#pdt_plot_final
add_summary(bp_cpm_pdt_sub_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(pain) %>%
  rstatix::shapiro_test(cpm_dif_pdt)

all_data %>%
  group_by(pain) %>%
  identify_outliers(cpm_dif_pdt) %>% select(id,pain,cpm_dif_pdt,is.outlier,is.extreme)
```
--> data are normal distributed
--> one extreme outlier


Test for equal variances
```{r}
sub_cpm_dif_pdt_variance <- if(all_data %>%
rstatix::levene_test(cpm_dif_pdt ~ pain) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
rstatix::levene_test(cpm_dif_pdt ~ pain)
```


T-tets and wilcox test
```{r}
all_data %>% rstatix::t_test(
         cpm_dif_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_cpm_dif_pdt_variance)
all_data %>% rstatix::wilcox_test(
         cpm_dif_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```
--> t-test: no sig differences
--> wilcox test: sig dif between:	Cov_pain and	HC



Sensitivity  analysis 
```{r}
sub_cpm_dif_pdt_id <- all_data %>%
  group_by(pain) %>%
  identify_outliers(cpm_dif_pdt) %>% filter(is.extreme == TRUE) %>% pull(id)

all_data%>% filter(!id %in% sub_cpm_dif_pdt_id) %>% rstatix::t_test(
         cpm_dif_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_cpm_dif_pdt_variance)
all_data %>% filter(!id %in% sub_cpm_dif_pdt_id) %>% rstatix::wilcox_test(
         cpm_dif_pdt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```

sensitivity analysis:
--> t-test: sig dif between:	Cov_no_pain and	HC
--> wilcox test: sif dif between: Cov_pain and	HC // and Cov_no_pain and	HC 

Get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data %>% rstatix::cohens_d(
  cpm_dif_pdt ~ pain,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = sub_cpm_dif_pdt_variance,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

Get effect size and bootstrapped ci (sensitivity analysis)
```{r}
set.seed(777)
all_data %>% filter(!id %in% sub_cpm_dif_pdt_id) %>% rstatix::cohens_d(
  cpm_dif_pdt ~ pain,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = sub_cpm_dif_pdt_variance,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```
CAVE: conf intervals include zero


#########################  CPM PTT 

Create plot
```{r}
bp_cpm_ptt_sub <- ggviolin(all_data, x = "pain", y = "cpm_dif_ptt",
   fill = "pain",
   palette = c("#00AFBB","#FC4E07","red"),
   color = "pain",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "CPM PTT values for post-covid patients and healthy controls",
  xlab = c("Group"),
  ylab = c("CPM PTT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_pain","Cov_pain")) + rremove("legend")

bp_cpm_ptt_sub_final <- ggpar(bp_cpm_ptt_sub, ylim = c(-30,100))
#ptt_plot_final
add_summary(bp_cpm_ptt_sub_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(pain) %>%
  rstatix::shapiro_test(cpm_dif_ptt)

 all_data %>%
  group_by(pain) %>%
  identify_outliers(cpm_dif_ptt) %>% select(id,pain,cpm_dif_ptt,is.outlier,is.extreme)

```
--> HC data not normal distributed
--> No extreme outlier

Test for equal variances
```{r}
sub_cpm_dif_ptt_variance <- if(all_data %>%
rstatix::levene_test(cpm_dif_ptt ~ pain) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
rstatix::levene_test(cpm_dif_ptt ~ pain)
```

T-test and wilcox test
```{r}
all_data %>% rstatix::t_test(
         cpm_dif_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = sub_cpm_dif_ptt_variance)

all_data %>% rstatix::wilcox_test(
         cpm_dif_ptt ~ pain, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)

```
--> Nothing significant

