---
title: "Ifatico Pain"
author: "JR"
date: "2024-07-29"
output: html_document
---

load packages
```{r message=FALSE, warning=FALSE}
library(compareGroups)
library(PairedData)
library(readxl)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(Rmisc) 
library(readxl)
library(ggpubr) 
library(rstatix) 
library(WRS2)
library(dplyr) 
library(effectsize)
library(dplyr)
library(MOTE)
library(colorspace)
library(readr)
```


Load data
```{r}
all_data <- readRDS(file = "all_data.rds")
```

```{r}
table(all_data$mecfs)
```


###################   PDT

Create plot 
```{r}
bp_fatigue_mecfs_pdt <- ggviolin(all_data, x = "mecfs", y = "qst_cuff_1_pdt",
   fill = "mecfs",
   palette = c("#00AFBB","springgreen","springgreen3"),
   color = "mecfs",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "PDT values for MECFS Yes/ No and healhy controls",
  xlab = c("Group"),
  ylab = c("PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_mecfs","Cov_mecfs")) + rremove("legend")

bp_fatigue_mecfs_pdt_final <- ggpar(bp_fatigue_mecfs_pdt, ylim = c(0,100))
#pdt_plot_final
add_summary(bp_fatigue_mecfs_pdt_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(mecfs) %>%
  rstatix::shapiro_test(qst_cuff_1_pdt)

all_data %>%
  group_by(mecfs) %>%
  identify_outliers(qst_cuff_1_pdt) %>% select(id,mecfs,qst_cuff_1_pdt,is.outlier,is.extreme)

```
Cov_mecfs data not normal distributed
no extreme outliers 

Test for equal variances
```{r}
aov_pdt_mecfs_pdt_var <- if(all_data %>% 
rstatix::levene_test(qst_cuff_1_pdt ~ f_group) %>% select(p) > 0.05){TRUE} else {FALSE}

all_data %>%
 rstatix::levene_test(qst_cuff_1_pdt ~ mecfs)
```

var are equal 

Anova and Kruskal test
```{r}
aov_pdt_mecfs_pdt <- anova_test(qst_cuff_1_pdt ~ mecfs, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_pdt_mecfs_pdt, correction = "auto")
rstatix::kruskal_test(qst_cuff_1_pdt ~ mecfs, data = all_data)
```
Kurskal Wallis and Anova are both significant

T-test and wilcox test
```{r}
all_data %>% t_test(
         qst_cuff_1_pdt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", var.equal = aov_pdt_mecfs_pdt_var)
all_data  %>% rstatix::wilcox_test(
         qst_cuff_1_pdt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

--> HC differs significantly from both groups (t test and wilcox)
--> No sig dif between Cov_no_mecfs and cov_mecfs


Get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  qst_cuff_1_pdt ~ mecfs,
  comparisons = NULL,
  ref.group = "HC",
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```


###################### PTT

Create plot
```{r}
bp_fatigue_mecfs_ptt <- ggviolin(all_data, x = "mecfs", y = "qst_cuff_1_ptt",
   fill = "mecfs",
   palette = c("#00AFBB","springgreen","springgreen3"),
   color = "mecfs",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "PTT values for MECFS Yes/ No and healhy controls",
  xlab = c("Group"),
  ylab = c("PTT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_mecfs","Cov_mecfs")) + rremove("legend")

bp_fatigue_mecfs_ptt_final <- ggpar(bp_fatigue_mecfs_ptt, ylim = c(0,100))
#ptt_plot_final
add_summary(bp_fatigue_mecfs_ptt_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(mecfs) %>%
  rstatix::shapiro_test(qst_cuff_1_ptt)

 all_data %>%
  group_by(mecfs) %>%
  identify_outliers(qst_cuff_1_ptt) %>% select(id,mecfs,qst_cuff_1_ptt,is.outlier,is.extreme)
```
--> Cov_mecfs and HC are not normal distributed 
--> No outlier

Test for equal variances
```{r}
aov_mecfs_ptt_var <-  if(all_data %>%
rstatix::levene_test(qst_cuff_1_ptt ~ mecfs) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
 rstatix::levene_test(qst_cuff_1_ptt ~ mecfs)
```
--> var are equal


Anova and Kruskal test
```{r}
aov_ptt_mecfs_ptt <- anova_test(qst_cuff_1_ptt ~ mecfs, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_ptt_mecfs_ptt, correction = "auto")
rstatix::kruskal_test(qst_cuff_1_ptt ~ mecfs, data = all_data)
```
Kruskal-Wallis and anova are significant

T-test and Wilcox test
```{r}
all_data  %>% rstatix::t_test(
         qst_cuff_1_ptt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_mecfs_ptt_var)
all_data  %>% rstatix::wilcox_test(
         qst_cuff_1_ptt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```


--> HC sig different to Cov_no_mecfs and Cov_mecfs (wilcox and t-test)
--> No difference between Cov_no_mecfs and Cov_mecfs (wilcox and t-test)

Get effect size and bootstrapped ci 
```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  qst_cuff_1_ptt ~ mecfs,
  comparisons = NULL,
  ref.group = "HC",
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```


################### SSP PDT

Create Plot
```{r}
bp_fatigue_mecfs_pdt <- ggviolin(all_data, x = "mecfs", y = "ssp_ratio_pdt",
   fill = "mecfs",
   palette = c("#00AFBB","springgreen","springgreen3"),
   color = "mecfs",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "SSP PDT values for MECFS Yes/ No and healhy controls",
  xlab = c("Group"),
  ylab = c("SSP PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_mecfs","Cov_mecfs")) + rremove("legend")

bp_fatigue_mecfs_pdt_final <- ggpar(bp_fatigue_mecfs_pdt, ylim = c(0,3))
#pdt_plot_final
add_summary(bp_fatigue_mecfs_pdt_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(mecfs) %>%
  rstatix::shapiro_test(ssp_ratio_pdt)

all_data %>%
  group_by(mecfs) %>%
  identify_outliers(ssp_ratio_pdt) %>% select(id,mecfs,ssp_ratio_pdt,is.outlier,is.extreme)

```
--> data are not normal distributed
--> 2 extreme outlier


Test for equal variances
```{r}
all_data %>%
 rstatix::levene_test(ssp_ratio_pdt ~ mecfs)
```
--> var are equal

ANova and Kruskal test
```{r}
aov_pdt_mecfs_ssp_pdt <- anova_test(ssp_ratio_pdt ~ mecfs, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_pdt_mecfs_ssp_pdt, correction = "auto")
rstatix::kruskal_test(ssp_ratio_pdt ~ mecfs, data = all_data)
```
--> Kruskal-Wallis and anova both not significant 

Sensitivity analysis
```{r}
mecfs_ssp_pdt_out_id <- all_data %>% group_by(mecfs) %>% identify_outliers(ssp_ratio_pdt) %>%
                                     filter(is.extreme == TRUE) %>% pull(id)

aov_pdt_mecfs_ssp_pdt_out <- all_data  %>% filter(!id %in% mecfs_ssp_pdt_out_id) %>%
anova_test(ssp_ratio_pdt ~ mecfs, detailed = TRUE)
rstatix::get_anova_table(aov_pdt_mecfs_ssp_pdt_out, correction = "auto")
all_data  %>% filter(!id %in% mecfs_ssp_pdt_out_id) %>%rstatix::kruskal_test(ssp_ratio_pdt ~ mecfs)
```
--> Sensitivity analysis no dif. Both still not significant



######################  SSP PTT

Create Plot
```{r}
bp_fatigue_mecfs_ptt <- ggviolin(all_data, x = "mecfs", y = "ssp_ratio_ptt",
   fill = "mecfs",
   palette = c("#00AFBB","springgreen","springgreen3"),
   color = "mecfs",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "SSP PTT values for MECFS Yes/ No and healhy controls",
  xlab = c("Group"),
  ylab = c("SSP PTT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_mecfs","Cov_mecfs")) + rremove("legend")

bp_fatigue_mecfs_ptt_final <- ggpar(bp_fatigue_mecfs_ptt, ylim = c(0,3))
#ptt_plot_final
add_summary(bp_fatigue_mecfs_ptt_final, "mean", color = "black",size = 0.5)
```


Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(mecfs) %>%
  rstatix::shapiro_test(ssp_ratio_ptt)

all_data %>%
  group_by(mecfs) %>%
  identify_outliers(ssp_ratio_ptt) %>% select(id,mecfs,ssp_ratio_ptt,is.outlier,is.extreme)
```
--> only Cov_mecfs normal distributed
--> 2 extreme outlier


Anova and Kruskal test 
```{r}
aov_mecfs_ssp_ptt_var <- if(all_data %>%
rstatix::levene_test(ssp_ratio_ptt ~ mecfs) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
 rstatix::levene_test(ssp_ratio_ptt ~ mecfs)
```
--> var are equal


Anova and Kruskal
```{r}
aov_ptt_mecfs_ssp_ptt <- anova_test(ssp_ratio_ptt ~ mecfs, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_ptt_mecfs_ssp_ptt, correction = "auto")
rstatix::kruskal_test(ssp_ratio_ptt ~ mecfs, data = all_data)
```
--> Kruskal-Wallis and ANova are sig.

T-test and wilcox test
```{r}
all_data  %>% rstatix::t_test(
         ssp_ratio_ptt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_mecfs_ssp_ptt_var)
all_data  %>% rstatix::wilcox_test(
         ssp_ratio_ptt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```
--> t_test : sig dif for Cov_mecfs vs	Cov_no_mecfs  and  Cov_mecfs vs. HC
--> wilcox_test: sig dif for Cov_mecfs vs	HC


Sensitivity anlaysis (anova and Kruskal)
```{r}
ptt_mecfs_ssp_ptt_out_id <- all_data %>% group_by(mecfs) %>% identify_outliers(ssp_ratio_ptt) %>%
                                        filter(is.extreme == TRUE) %>% pull(id)

aov_ptt_mecfs_ssp_ptt_out <- all_data %>% filter(!id %in% ptt_mecfs_ssp_ptt_out_id) %>%
anova_test(ssp_ratio_ptt ~ mecfs, detailed = TRUE)
rstatix::get_anova_table(aov_ptt_mecfs_ssp_ptt_out, correction = "auto")
all_data %>% filter(!id %in% ptt_mecfs_ssp_ptt_out_id) %>% rstatix::kruskal_test(ssp_ratio_ptt ~ mecfs)
```
--> sensitivity analysis: still both significant

Sensitivity analysis t-test and wilcox test
```{r}
all_data  %>% filter(!id %in% ptt_mecfs_ssp_ptt_out_id) %>% rstatix::t_test(
         ssp_ratio_ptt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_mecfs_ssp_ptt_var)
all_data  %>% filter(!id %in% ptt_mecfs_ssp_ptt_out_id) %>% rstatix::wilcox_test(
         ssp_ratio_ptt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

Sensitivity analysis: Now both wilcox and t_test: sif dif for Cov_mecfs	vs HC

Get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  ssp_ratio_ptt ~ mecfs,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

Get effect size and bootstrapped ci (sensitivity analysis)
```{r}
set.seed(777)
all_data %>% filter(!id %in% ptt_mecfs_ssp_ptt_out_id) %>% rstatix::cohens_d(
  ssp_ratio_ptt ~ mecfs,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```


######################  CPM  PDT

Create Plot
```{r}
bp_fatigue_mecfs_cpm_pdt <- ggviolin(all_data, x = "mecfs", y = "cpm_dif_pdt",
   fill = "mecfs",
   palette = c("#00AFBB","springgreen","springgreen3"),
   color = "mecfs",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "SSP PDT values for MECFS Yes/ No and healhy controls",
  xlab = c("Group"),
  ylab = c("SSP PDT"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_mecfs","Cov_mecfs")) + rremove("legend")

bp_fatigue_mecfs_cpm_pdt_final <- ggpar(bp_fatigue_mecfs_cpm_pdt, ylim = c(-25,50))
#pdt_plot_final
add_summary(bp_fatigue_mecfs_cpm_pdt_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution 
```{r}
all_data %>%
  dplyr::group_by(mecfs) %>%
  rstatix::shapiro_test(cpm_dif_pdt)

all_data %>%
  group_by(mecfs) %>%
  identify_outliers(cpm_dif_pdt) %>% select(id,mecfs,cpm_dif_pdt,is.outlier,is.extreme)

```
--> only Cov_no_mecfs data normal distributed
--> 2 extreme outlier

Test for equal variances
```{r}
aov_mecfs_cpm_pdt_var <- if(all_data %>%
rstatix::levene_test(cpm_dif_pdt ~ mecfs) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
 rstatix::levene_test(cpm_dif_pdt ~ mecfs)
```
--> var are equal

Anova and Kruskal test
```{r}
aov_pdt_mecfs_cpm_pdt <- anova_test(cpm_dif_pdt ~ mecfs, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_pdt_mecfs_cpm_pdt, correction = "auto")
rstatix::kruskal_test(cpm_dif_pdt ~ mecfs, data = all_data)
```
Anova not sig but kruskal wallis is 

T-test and wilcox test
```{r}
all_data  %>% rstatix::t_test(
         cpm_dif_pdt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_mecfs_cpm_pdt_var)
all_data  %>% rstatix::wilcox_test(
         cpm_dif_pdt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```
only wilcox test sig dif for Cov_mecfs vs HC


Sensitivity analysis (anova and kruskal)
```{r}
mecfs_cpm_pdt_out_id <- all_data %>% group_by(mecfs) %>% identify_outliers(cpm_dif_pdt) %>%
                                     filter(is.extreme == TRUE) %>% pull(id)
aov_pdt_mecfs_cpm_pdt_out <- all_data  %>% filter(!id %in% mecfs_cpm_pdt_out_id) %>%
anova_test(cpm_dif_pdt ~ mecfs, detailed = TRUE)
rstatix::get_anova_table(aov_pdt_mecfs_cpm_pdt_out, correction = "auto")
all_data  %>% filter(!id %in% mecfs_cpm_pdt_out_id)  %>%rstatix::kruskal_test(cpm_dif_pdt ~ mecfs)
```
Sensitivity analysis: no dif (Anova not sig but kruskal wallis is )

Sensitivity analysis (t-test and wilcox test)
```{r}
all_data %>% filter(!id %in% mecfs_cpm_pdt_out_id) %>% rstatix::t_test(
         cpm_dif_pdt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_mecfs_cpm_pdt_var)
all_data %>% filter(!id %in% mecfs_cpm_pdt_out_id) %>% rstatix::wilcox_test(
         cpm_dif_pdt ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

sensitivity analysis: wilcox test additionaly sig results for Cov_no_mecfs vs	HC


Get effect size and bootstrapped ci
```{r}
set.seed(777)
all_data   %>% rstatix::cohens_d(
  cpm_dif_pdt ~ mecfs,
  comparisons = NULL,
  ref.group = "HC",
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```


Get effect size and bootstrapped ci (sensitivity analysis)
```{r}
set.seed(777)
all_data  %>% filter(!id %in% mecfs_cpm_pdt_out_id)  %>% rstatix::cohens_d(
  cpm_dif_pdt ~ mecfs,
  comparisons = NULL,
  ref.group = "HC",
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```


############################## CPM PTT

Create plot 
```{r}
bp_fatigue_mecfs_cpm_ptt <- ggviolin(all_data, x = "mecfs", y = "cpm_dif_ptt",
   fill = "mecfs",
   palette = c("#00AFBB","springgreen","springgreen3"),
   color = "mecfs",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "CPM ptt values for MECFS Yes/ No and healhy controls",
  xlab = c("Group"),
  ylab = c("CPM ptt"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_mecfs","Cov_mecfs")) + rremove("legend")

bp_fatigue_mecfs_cpm_ptt_final <- ggpar(bp_fatigue_mecfs_cpm_ptt, ylim = c(-25,50))
#ptt_plot_final
add_summary(bp_fatigue_mecfs_cpm_ptt_final, "mean", color = "black",size = 0.5)
```

Search for extreme outlier and test for normal distribution 
```{r}
all_data %>%
  dplyr::group_by(mecfs) %>%
  rstatix::shapiro_test(cpm_dif_ptt)

all_data %>%
  group_by(mecfs) %>%
  identify_outliers(cpm_dif_ptt) %>% select(id,mecfs,cpm_dif_ptt,is.outlier,is.extreme)


```
--> HC data not normal distributed
--> no extrem outlier


Test for euqal variances
```{r}
all_data %>%
 rstatix::levene_test(cpm_dif_ptt ~ mecfs)
```
--> var are equal


Anova and kruskal test
```{r}
aov_ptt_mecfs_cpm_ptt <- anova_test(cpm_dif_ptt ~ mecfs, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_ptt_mecfs_cpm_ptt, correction = "auto")
rstatix::kruskal_test(cpm_dif_ptt ~ mecfs, data = all_data)
```
anova and kruskal wallis both not significant


##############   TSP ##########################################


Cretae long df to crete line plot
```{r}
tsp_line_long <- all_data %>% select(id,gruppe,pain,f_group,mecfs,qst_temporal_1:qst_temporal_10) %>% pivot_longer(cols = qst_temporal_1:qst_temporal_10,names_to = "timepoint",values_to = "VAS.Rating") %>% mutate(timepoint = sub("qst_temporal_","",timepoint))
```

Create line plot 

```{r}
tsp_line_plot4 <- ggline(tsp_line_long, x = "timepoint", y = "VAS.Rating", color = "mecfs",
 add = "mean_se", palette = c("springgreen3","springgreen","#00AFBB")) 

tsp_line_plot4 <- ggpar(tsp_line_plot4, ylim = c(0,10))
tsp_line_plot4
```

Create plot 
```{r}
bp_tsp_mecfs <- ggviolin(all_data, x = "mecfs", y = "tsp",
   fill = "mecfs",
   palette = c("#00AFBB","springgreen","springgreen3"),
   color = "mecfs",
   alpha = 0.9,
   add = c("boxplot"), #"jitter"
   add.params = list(fill = "white", color = "black",size = 1),
   title = "TSP values for MECFS Yes/ No and healhy controls",
  xlab = c("Group"),
  ylab = c("TSP"),
  trim = TRUE,
  #legend = FALSE,
 
  order = c("HC","Cov_no_mecfs","Cov_mecfs")) + rremove("legend")

bp_tsp_mecfs_final <- ggpar(bp_tsp_mecfs, ylim = c(-10,10))
#pdt_plot_final
add_summary(bp_tsp_mecfs_final, "mean", color = "black",size = 0.5)
```
Search for extreme outlier and test for normal distribution
```{r}
all_data %>%
  dplyr::group_by(mecfs) %>%
  rstatix::shapiro_test(tsp)

all_data %>%
  group_by(mecfs) %>%
  identify_outliers(tsp) %>% select(id,mecfs,tsp,is.outlier,is.extreme)

```
--> Cov_mecfs datat not normal distributed
--> one extreme outlier

Test for equal variances
```{r}
aov_mecfs_tsp_var <- if(all_data %>%
rstatix::levene_test(tsp ~ mecfs) %>% select(p) > 0.05){TRUE} else {FALSE}
all_data %>%
 rstatix::levene_test(tsp ~ mecfs)
```
--> var are equal

Anova and Kruskal test
```{r}
aov_pdt_mecfs_tsp <- anova_test(tsp ~ mecfs, data = all_data, detailed = TRUE)
rstatix::get_anova_table(aov_pdt_mecfs_tsp, correction = "auto")
rstatix::kruskal_test(tsp ~ mecfs, data = all_data)
```
both tests are significant

T-test and Wilcox test
```{r}
all_data %>% rstatix::t_test(
         tsp ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_mecfs_tsp_var)
all_data %>% rstatix::wilcox_test(
         tsp ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

WIlcox and t-test: sig results for Cov_no_mecfs	 vs HC


Sensitivity analysis (anova and kruskal)
```{r}
mecfs_tsp_out_id <- all_data %>% group_by(mecfs) %>% identify_outliers(tsp) %>% 
                                 filter(is.extreme == TRUE) %>% pull(id)
aov_mecfs_tsp_out <- all_data  %>% filter(!id %in% mecfs_tsp_out_id) %>%
anova_test(tsp ~ mecfs, detailed = TRUE)
rstatix::get_anova_table(aov_mecfs_tsp_out, correction = "auto")
all_data   %>% filter(!id %in% mecfs_tsp_out_id) %>%rstatix::kruskal_test(tsp ~ mecfs)
```
--> sensitivity analysis: both still significant


Sensitivity analysis (t-test and wilcox test)
```{r}
all_data  %>% filter(!id %in% mecfs_tsp_out_id) %>% rstatix::t_test(
         tsp ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE, var.equal = aov_mecfs_tsp_var)
all_data  %>% filter(!id %in% mecfs_tsp_out_id) %>% rstatix::wilcox_test(
         tsp ~ mecfs, paired = FALSE, 
         p.adjust.method = "none", detailed = FALSE)
```

--> sensitivity analysis: no dif (sig results for Cov_no_mecfs	vs HC)


Get effectsize and bootstrapped ci
```{r}
set.seed(777)
all_data  %>% filter(mecfs != "Cov_mecfs") %>% mutate(mecfs = droplevels(mecfs)) %>% rstatix::cohens_d(
  tsp ~ mecfs,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```

Get effectsize and bootstrapped ci (sensitivity analysis)
```{r}
set.seed(777)
all_data  %>% filter(!id %in% mecfs_tsp_out_id) %>% filter(mecfs != "Cov_mecfs") %>% mutate(mecfs = droplevels(mecfs)) %>% rstatix::cohens_d(
  tsp ~ mecfs,
  comparisons = NULL,
  ref.group = NULL,
  paired = FALSE,
 # mu = 0,
  var.equal = TRUE,
  hedges.correction = FALSE,
  ci = TRUE,
  conf.level = 0.95,
  ci.type = "bca",
  nboot = 10000
)
```









