---
title: "Code Rel FMS t2 (prepare data)"
author: "JR"
date: "2025-03-30"
output: html_document
---


```{r}
library(dplyr)
library(tidyr)
library(readr)
data_t1 <- read_csv("fms_edges_t1.csv")
data_t2 <- read_csv("fms_edges_t2.csv")
```


```{r}
data_t2 <- data_t2 %>% filter(eingabe_edges_t2_complete == 2) 
data_t1 <- data_t1 %>% filter(record_id %in% data_t2$record_id)

data_t1$id <- 1:nrow(data_t1) 
data_t2$id <- 1:nrow(data_t2)

```

```{r}
data1 <- data_t1 %>% select(verwendetesymptome1___1:verwendetesymptome1___93)

names(data1) <- gsub("verwendetesymptome1___", "", names(data1), fixed = TRUE)

df1 <- t(apply(data1, 1, function(row) {
 
  ifelse(row == 1, colnames(data1)[which(row == 1)], row)
}))


df1 <- as.data.frame(df1)

df1 <- apply(df1, 2, as.numeric)
df1 <- as.data.frame(df1)

data1_final <- as.data.frame(rowSums(df1))
names(data1_final) <- "1"
data1_final$id <- 1:nrow(data1_final)
```

#2
```{r}
data2 <- data_t1 %>% select(verwendetesymptome2___1:verwendetesymptome2___93)

names(data2) <- gsub("verwendetesymptome2___", "", names(data2), fixed = TRUE)

df2 <- t(apply(data2, 1, function(row) {
 
  ifelse(row == 1, colnames(data2)[which(row == 1)], row)
}))


df2 <- as.data.frame(df2)

df2 <- apply(df2, 2, as.numeric)
df2 <- as.data.frame(df2)

data2_final <- as.data.frame(rowSums(df2))
names(data2_final) <- "2"
data2_final$id <- 1:nrow(data2_final)
```

```{r}
data3 <- data_t1 %>% select(verwendetesymptome3___1:verwendetesymptome3___93)

names(data3) <- gsub("verwendetesymptome3___", "", names(data3), fixed = TRUE)

df3 <- t(apply(data3, 1, function(row) {
 
  ifelse(row == 1, colnames(data3)[which(row == 1)], row)
}))


df3 <- as.data.frame(df3)

df3 <- apply(df3, 2, as.numeric)
df3 <- as.data.frame(df3)

data3_final <- as.data.frame(rowSums(df3))
names(data3_final) <- "3"
data3_final$id <- 1:nrow(data3_final)
```

```{r}
data4 <- data_t1 %>% select(verwendetesymptome4___1:verwendetesymptome4___93)

names(data4) <- gsub("verwendetesymptome4___", "", names(data4), fixed = TRUE)

df4 <- t(apply(data4, 1, function(row) {
 
  ifelse(row == 1, colnames(data4)[which(row == 1)], row)
}))


df4 <- as.data.frame(df4)

df4 <- apply(df4, 2, as.numeric)
df4 <- as.data.frame(df4)

data4_final <- as.data.frame(rowSums(df4))
names(data4_final) <- "4"
data4_final$id <- 1:nrow(data4_final)
```

```{r}
data5 <- data_t1 %>% select(verwendetesymptome5___1:verwendetesymptome5___93)

names(data5) <- gsub("verwendetesymptome5___", "", names(data5), fixed = TRUE)

df5 <- t(apply(data5, 1, function(row) {
 
  ifelse(row == 1, colnames(data5)[which(row == 1)], row)
}))


df5 <- as.data.frame(df5)

df5 <- apply(df5, 2, as.numeric)
df5 <- as.data.frame(df5)

data5_final <- as.data.frame(rowSums(df5))
names(data5_final) <- "5"
data5_final$id <- 1:nrow(data5_final)
```


```{r}
data6 <- data_t1 %>% select(verwendetesymptome6___1:verwendetesymptome6___93)

names(data6) <- gsub("verwendetesymptome6___", "", names(data6), fixed = TRUE)

df6 <- t(apply(data6, 1, function(row) {
  
  ifelse(row == 1, colnames(data6)[which(row == 1)], row)
}))


df6 <- as.data.frame(df6)

df6 <- apply(df6, 2, as.numeric)
df6 <- as.data.frame(df6)

data6_final <- as.data.frame(rowSums(df6))
names(data6_final) <- "6"
data6_final$id <- 1:nrow(data6_final)
```


```{r}
data7 <- data_t1 %>% select(verwendetesymptome7___1:verwendetesymptome7___93)

names(data7) <- gsub("verwendetesymptome7___", "", names(data7), fixed = TRUE)

df7 <- t(apply(data7, 1, function(row) {
 
  ifelse(row == 1, colnames(data7)[which(row == 1)], row)
}))


df7 <- as.data.frame(df7)

df7 <- apply(df7, 2, as.numeric)
df7 <- as.data.frame(df7)

data7_final <- as.data.frame(rowSums(df7))
names(data7_final) <- "7"
data7_final$id <- 1:nrow(data7_final)
```

```{r}
data8 <- data_t1 %>% select(verwendetesymptome8___1:verwendetesymptome8___93)

names(data8) <- gsub("verwendetesymptome8___", "", names(data8), fixed = TRUE)

df8 <- t(apply(data8, 1, function(row) {
  
  ifelse(row == 1, colnames(data8)[which(row == 1)], row)
}))


df8 <- as.data.frame(df8)

df8 <- apply(df8, 2, as.numeric)
df8 <- as.data.frame(df8)

data8_final <- as.data.frame(rowSums(df8))
names(data8_final) <- "8"
data8_final$id <- 1:nrow(data8_final)
```

```{r}
data9 <- data_t1 %>% select(verwendetesymptome9___1:verwendetesymptome9___93)

names(data9) <- gsub("verwendetesymptome9___", "", names(data9), fixed = TRUE)

df9 <- t(apply(data9, 1, function(row) {
 
  ifelse(row == 1, colnames(data9)[which(row == 1)], row)
}))


df9 <- as.data.frame(df9)

df9 <- apply(df9, 2, as.numeric)
df9 <- as.data.frame(df9)

data9_final <- as.data.frame(rowSums(df9))
names(data9_final) <- "9"
data9_final$id <- 1:nrow(data9_final)
```


```{r}
data10 <- data_t1 %>% select(verwendetesymptome10___1:verwendetesymptome10___93)

names(data10) <- gsub("verwendetesymptome10___", "", names(data10), fixed = TRUE)

df10 <- t(apply(data10, 1, function(row) {
  
  ifelse(row == 1, colnames(data10)[which(row == 1)], row)
}))


df10 <- as.data.frame(df10)

df10 <- apply(df10, 2, as.numeric)
df10 <- as.data.frame(df10)

data10_final <- as.data.frame(rowSums(df10))
names(data10_final) <- "10"
data10_final$id <- 1:nrow(data10_final)
```


```{r}
merged_data <- Reduce(function(x, y) merge(x, y, by = "id", all = TRUE), list(data1_final,data2_final,data3_final,data4_final,data5_final,data6_final,
    data7_final,data8_final,data9_final,data10_final))
```



```{r}

edges_data <- data_t2 %>% select(edge01_t2:edge90_t2,id)
colnames(edges_data) <- sub('_t2','',colnames(edges_data))
```


```{r}

edges_long <- tidyr::pivot_longer(edges_data, cols = -id, names_to = NULL) %>%
  separate(value, into = c("part1", "part2"), sep = "-", extra = "merge")
```


```{r}
edges_long$na_check <- is.na(edges_long$part1) & is.na(edges_long$part2)
edges_long <- edges_long %>% filter(na_check == FALSE) %>% select(-na_check) # dont use drop in a in case some edges are wrong
```


```{r}
test_numeric <- as.numeric(edges_long$part2)
which(is.na(test_numeric))

```



```{r}

edges_wide <- tidyr::pivot_wider(edges_long, names_from = part1, values_from = part2)
```


```{r}
cn <- colnames(edges_wide)
pattern <- "^\\d+_\\d+$"
# Find column names that DO NOT match the pattern
non_matching_cols <- cn[!grepl(pattern, cn)]
non_matching_cols_id <- non_matching_cols[-(which(non_matching_cols == "id"))]
```


```{r}
ew <- edges_wide %>%
                     mutate(across(where(is.list), ~ lapply(.,function(x) if (is.null(x)) NA else x))) %>% 
                     mutate(across(where(is.list), unlist))

ew <- apply(ew, 2, as.numeric)
ew <- as.data.frame(ew)
```



```{r}

nodes_long <- tidyr::pivot_longer(merged_data, cols = -id, names_to = "delete", values_to = "names")

nodes_long <- nodes_long %>% select(-delete)
# Create a dummy value column with a constant value of 1 to indicate the presence of each value
nodes_long$value <- 1
nodes_long <- nodes_long %>% filter(names != 0)


nodes_wide <- tidyr::pivot_wider(nodes_long, names_from = names, values_from = value)
nw <- nodes_wide %>% mutate(across(where(is.list), ~ lapply(.,function(x) if (is.null(x)) NA else x))) %>% 
                     mutate(across(where(is.list), unlist))
```



```{r}
n_names <- colnames(nw)
n_names <- n_names[-(which(n_names == "id"))]
```

```{r}
werte <- data_t1 %>% select(id,wert_1:wert_93) 
```

```{r}
nw2 <- nw
for (i in n_names) {
     for (j in nw2$id) {
    if(!is.na(nw2[which(nw2$id == j),i])){
      if(is.na(werte[[which(werte$id == j), paste0("wert_",i)]])){nw2[which(nw2$id == j),i] <- 99999}
      else{nw2[which(nw2$id == j),i] <- werte[[which(werte$id == j), paste0("wert_",i)]]}
      }
     }
}
```

```{r}
which(nw2 == 99999, arr.ind = TRUE)
```

# They worked in both interviews with a symptom that was not selected before. Insert 400 (half of possible importance score) as a dummy.
Not relevant for the analysis for this paper!

```{r}
nw[27,45] <- 1
nw2[27,45] <- 400  
```


check whether back-transformation is equal
```{r}
nw_check <- nw2
nw_check[!is.na(nw_check)] <- 1
nw_check$id <- nw2$id
identical(nw_check,nw)
all.equal(nw_check,nw)
```

```{r}
data_new <- merge(nw2,ew, by = "id", all = TRUE)
```

Delete edges which consists of one added node by the participant as we cannot interpret them
```{r}
cols_to_drop <- grep("(^94|94$|^95|95$|^96|96$|^97|97$|^98|98$|^99|99$|^100|100$|^101|101$|^102|102$|^103|103$|^104|104$)", colnames(data_new), value = TRUE)
```

```{r}
data_new <- data_new %>% select(-all_of(cols_to_drop))
```


```{r}
library(PECAN2)
```

```{r}
which(colnames(data_new) == "80")
```

Check whether there are any edges without a corresponding node
```{r}

warning_log <- data.frame(
  id = integer(),
  warning_message = character(),
  stringsAsFactors = FALSE
)


participant_ids <- 1:50  


for (i in participant_ids) {

  result <- tryCatch(
    {
  
      pecanExtract(data = data_new, id_row = i,nodes = 2:74,edges = 75:ncol(data_new),edges_sep = "_")
      NULL  
    },
    warning = function(w) {
     
      warning_log <<- rbind(warning_log, data.frame(
        id = i,
        warning_message = conditionMessage(w),
        stringsAsFactors = FALSE
      ))
      return(NULL)  
    },
    error = function(e) {
     
      return(NULL)
    }
  )
}


print(warning_log)

```



```{r}
networks_rel_t2 <- list()
participant_ids <- 1:50  


for (i in participant_ids) {
  
      networks_rel_t2[[i]] <- pecanExtract(data = data_new, id_row = i,nodes = 2:74,edges = 75:ncol(data_new),edges_sep = "_")}
     
   

```

```{r}
names(networks_rel_t2) <- data_t2$record_id
```

```{r}
saveRDS(networks_rel_t2, file = "networks_rel_t2_fms170325.Rda" )
```
















































