---
title: "Cross Sectional Network Analysis"
author: "JR"
date: "03.04.25"
output: html_document
---



Load packages
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(readxl)
library(ggplot2)
library(networktools)
library(car)
library(NetworkComparisonTest)
library(igraph)
library(qgraph)
library(bootnet)
library(mgm)
library(EGAnet)
library(huge)
library(rempsyc)
library(viridis)
library(colorspace)
library(flextable)
library(officer)
```

Load data and variable names
```{r}
load("data_final2_100924.Rda")
load("vars_final2_100924.Rda")
```


Create df for nw.
```{r}
data_nw <- data_final2 %>% select(all_of(vars_final2)) %>% drop_na() 
```


Rename variables
```{r}
data_nw <- data_nw %>% dplyr::rename(
"Perceived.Health" = sf1,
"Pain.Impact" = sf8, 
"Social.Impact" = sf12,
"Dizziness" = phq1h,
"Fainting" = phq1i,
"Anhedonia" = phq2a,
"Appetite.Dysregulation" = phq2e,
"Self.Worth.Issues" = phq2f,
"Psychomotor.Changes" = phq2h,
"Suicidal.Ideation" = phq2i,
"Health.concerns" = phq12a, 
"Libido.Loss"= phq12c,
"Trauma.Memories" = phq12j,
"Panic.Attacks" =  phq3a,
"Concentration.Deficits" = phq2g,
"Reduced.Talking" =  ads10,
"Loneliness" =  ads11,
"Perceived.Social.Rejection" =  ads14,
"Loss.of.drive"= ads15,
"Heart.Palpitations" = phq1j,
"Shortness.Of.Breath" = phq1k,
"Self.Efficacy" = self_e,
"Daily.Living.Skills" = physical_imp,
"Pain.Distribution" = pain_symptoms,
"Pain.Severity" = pain_sev,
"Gastrointestinal.Discomfort" = gastro,
"Sleeping.Problems" = sleep_quality,
"Fatigue" = fatigue,
"Anxiety/Nervousness" = anxious,
"Depressed.mood" = depressed)
```


All variables that need bo be binarized
```{r}
vars_dich <- c("Dizziness","Fainting","Heart.Palpitations","Shortness.Of.Breath","Anhedonia","Appetite.Dysregulation","Self.Worth.Issues","Concentration.Deficits",
               "Psychomotor.Changes","Suicidal.Ideation","Health.concerns","Libido.Loss","Trauma.Memories","Reduced.Talking","Loneliness",
               "Perceived.Social.Rejection","Loss.of.drive","Panic.Attacks")
```

Statistics
```{r}
statistics <- list(Mean = ~round(mean(.x),2), SD = ~round(sd(.x),2), Min = ~round(min(.x),2), Max = ~round(max(.x),2))
```

Get stats table
```{r}
desc <- data_nw  %>% summarise_all(statistics) %>% 
                         pivot_longer(cols = everything(), names_to = c("node", ".value"), names_sep = "_")
```


Binarzize chosen variables
```{r}
data_nw <- data_nw %>%  mutate(Dizziness = ifelse(Dizziness > 0, 1, 0),
                               Fainting = ifelse(Fainting > 0, 1, 0),
                               Heart.Palpitations = ifelse(Heart.Palpitations > 0, 1, 0),
                               Shortness.Of.Breath = ifelse(Shortness.Of.Breath > 0, 1, 0),
                               Anhedonia = ifelse(Anhedonia > 1, 1, 0),
                               Appetite.Dysregulation = ifelse(Appetite.Dysregulation > 1, 1, 0),
                               Self.Worth.Issues = ifelse(Self.Worth.Issues > 1, 1, 0),
                               Concentration.Deficits = ifelse(Concentration.Deficits > 1, 1, 0),
                               Psychomotor.Changes = ifelse(Psychomotor.Changes > 1, 1, 0),
                               Suicidal.Ideation = ifelse(Suicidal.Ideation > 1, 1, 0),
                               Health.concerns = ifelse(Health.concerns > 0, 1, 0),
                               Libido.Loss = ifelse(Libido.Loss > 0, 1, 0),
                               Trauma.Memories = ifelse(Trauma.Memories > 0, 1, 0),
                              # ads5 = ifelse(ads5 > 1, 1, 0),
                               Reduced.Talking = ifelse(Reduced.Talking > 1, 1, 0),
                               Loneliness = ifelse(Loneliness > 1, 1, 0),
                               Perceived.Social.Rejection = ifelse(Perceived.Social.Rejection > 1, 1, 0),
                               Loss.of.drive = ifelse(Loss.of.drive > 1, 1, 0))
```


Get stats for binarized variables
```{r}
desc_dich <- data_nw %>% select((all_of(vars_dich))) %>% summarise_all(~sum(.x)) %>% 
                         pivot_longer(cols = everything(), names_to = c("node"), values_to = "Present") #%>% 
                       #  mutate(present = paste0(present,"/",nrow(data_nw)))
```

Add information how many items were used to create the variable
```{r}
comb_info <- data.frame(
  Node = c("Daily.Living.Skills","Fatigue","Sleeping.Problems","Anxiety/Nervousness","Depressed.mood","Self.Efficacy","Pain.Distribution","Gastrointestinal.Discomfort"), 
                    #    Combination.method = c("CFA","CFA","CFA","CFA","CFA","Mean","Sum Score","Sum Score"),
                        Number.of.items = c(19,4,3,4,7,8,5,2))
colnames(comb_info) <- gsub(pattern = '.', replacement = " ",colnames(comb_info),fixed = TRUE)
comb_info$Node <- gsub(pattern = '.', replacement = " ",comb_info$Node,fixed = TRUE)
```

Combine to descr table
```{r}
desc_combined <- merge(desc,desc_dich, by = "node",all = TRUE)
desc_combined[is.na(desc_combined)] <- ""
desc_combined$Phrasing <- ""
#desc_combined$'Combination method' <- ""
#desc_combined$'Number of items' <- ""

colnames(desc_combined)[1] <- "Node"
desc_combined$Node <- gsub(pattern = '.', replacement = " ",desc_combined$Node,fixed = TRUE)
desc_combined <- merge(desc_combined,comb_info, by = "Node",all = TRUE)
desc_combined <- desc_combined %>% select(1,7,8,everything())
desc_combined$`Number of items`[is.na(desc_combined$`Number of items`)] <- 1
desc_combined[is.na(desc_combined)] <- ""

```



Check how many NA waves are in the data and create table
```{r}
apa_tab <- nice_table(desc_combined,
           title = c("Descriptive statistic of the nodes"),
  note = "'Mean' = mean, 'SD' = standard deviation, 'Min' = minimum, 'Max' = maximum. 'Combination method' = The combination method (mean, sum score or conformatory factor analysis (CFA)) if multiple items were combined into one node. 'Number of items' = The number of combined items. 'Phrasing' = The phrasing of nodes represented by a single item. 'Present' = Number of patients in which the symptom was present if the item was binarized prior to the analysis (n = 3044)"
)
apa_tab
#print(apa_tab, preview = "docx")
```

Compare npn transformed nw with untransformed nw
```{r}
#nw_no_t <- estimateNetwork(data_nw,default = "mgm")
#plot(nw_no_t)

#vars_transform <- c("Perceived.Health", "Pain.Impact","Social.Impact","Gastrointestinal.Discomfort","Depressed.mood",
#                    "Anxiety/Nervousness","Sleeping.Problems","Self.Efficacy","Pain.Severity","Pain.Distribution","Daily.Living.Skills","Fatigue")

#data_nw_t <- data_nw

#for (var_name in vars_transform) {
#  
#  test_var <- data_nw_t[,var_name, drop = TRUE]
#  shapiro_test <- shapiro.test(test_var)
#  if (shapiro_test$p.value < 0.05){
#   data_nw_t[,var_name] <- as.vector(huge.npn(data_nw_t[,var_name, drop = FALSE]))
#  }}

#nw_t <- estimateNetwork(data_nw_t,default = "mgm")
#plot(nw_t)

#set.seed(777)
#nct_t_result <- NCT(nw_t,nw_no_t,
#                    it = 1000, 
#                    paired = TRUE,
#                    test.edges = FALSE,
#                    test.centrality = TRUE,
#                    abs = FALSE,
#                    centrality = c("strength", "expectedInfluence"))
#save(nct_t_result, file = "nct_t_result_100924.Rda")

load("nct_t_result_100924_nw_vs_nwt.Rda")
```




Compare diagnosis at prior and after 2010
```{r}
#data_nwa_og <- read_excel("data_nwa.xlsx")
#data_nwa_demo <- data_nwa_og %>% select(id,geschl,age,year_visit)
#data_demo2 <- merge(data_final2,data_nwa_demo, by = "id", all = TRUE) 
#data_demo2 <- data_demo2 %>% select(all_of(vars_final2),year_visit,geschl,age) %>% drop_na()
#data_pre2010 <- data_demo2 %>% filter(as.numeric(year_visit) <= 2010) %>% select(-year_visit) 
#data_post2010 <- data_demo2 %>% filter(as.numeric(year_visit) > 2010) %>% select(-year_visit) 
#table(data_pre2010$geschl)
#summary(data_pre2010$age)
#sd(data_pre2010$age)
#table(data_post2010$geschl)
#summary(data_post2010$age)
#sd(data_post2010$age)
#nw_pre2010 <- estimateNetwork(data_pre2010,default = "mgm")
#nw_post2010 <- estimateNetwork(data_post2010,default = "mgm")
#set.seed(777)
#nct_2010_result <- NCT(nw_pre2010,nw_post2010,
#                    it = 1000, 
#                    paired = FALSE,
#                    test.edges = FALSE,
#                    test.centrality = TRUE,
#                    abs = FALSE,
#                    centrality = c("strength", "expectedInfluence"))
#save(nct_2010_result, file = "nct_2010_result_100924.Rda")
load("nct_2010_result_100924.Rda")
summary(nct_t_result)
```


# not necessary but for a more easy phrasing
```{r}
nw <- estimateNetwork(data_nw,default = "mgm")
plot(nw)
```

```{r}
summary(nw)
```


```{r}
any(nw$graph < 0)
```
No negative edges


```{r}
com_mgm <- EGAnet::community.detection(nw$graph,algorithm = "walktrap", allow.singleton = TRUE)
coms <- as.data.frame(com_mgm)
coms$name <- colnames(data_nw)
coms
EGAnet::community.detection(nw$graph,algorithm = "walktrap", allow.singleton = TRUE)
```

Set color for the communities
```{r}
coms$color <- car::recode(coms$x,
"1 = '#F0F921FF';
2 = '#5D01A6FF';
3 = '#9C179EFF';
4 = '#CC4678FF';
5 = '#ED7953FF';
6 = '#FDB32FFF';
7 = '#0D0887FF'") 
```


```{r}
oc1 <- "#F0F921FF"
oc2 <-  '#5D01A6FF'
oc3 <- '#9C179EFF'
oc4 <- '#CC4678FF'
oc5 <- '#ED7953FF'
oc6 <- '#FDB32FFF'
oc7 <- '#0D0887FF'
```


Estimate prdictability
```{r}
nw_predict <- mgm(as.matrix(data_nw),
           type = nw$results$call$type, 
           level = nw$results$call$level, 
           lambdaSel = "EBIC",
           binarySign = TRUE
           )
```

```{r}
pre_mgm <- predict(nw_predict, data = as.matrix(data_nw), errorCon = c("R2"), errorCat = c("CC", "nCC", "CCmarg"))
```


```{r}
error_list <- list()
for(i in 1:30){
if(is.na(pre_mgm$errors[i,2])){
   error_list[[i]] <- c(pre_mgm$errors[i,5],(pre_mgm$errors[i,3] - pre_mgm$errors[i,5]))
}  
else
{error_list[[i]] <- pre_mgm$errors[i,2]}}
```

Color predictablity
```{r}
color_list <- list() # List for Colors
for(i in 1:30){ 
if(is.na(pre_mgm$errors[i,2])){
  if(coms[i,1] == 1){color_list[[i]] <- c(lighten(oc1,space = "combined",amount = 0.3),darken(oc1,space = "HCL",amount = 0.2))}
  if(coms[i,1] == 2){color_list[[i]] <- c(lighten(oc2,space = "combined",amount = 0.3),darken(oc2,space = "HCL",amount = 0.2))}
  if(coms[i,1] == 3){color_list[[i]] <- c(lighten(oc3,space = "combined",amount = 0.3),darken(oc3,space = "HCL",amount = 0.2))}
  if(coms[i,1] == 4){color_list[[i]] <- c(lighten(oc4,space = "combined",amount = 0.3),darken(oc4,space = "HCL",amount = 0.2))}
  if(coms[i,1] == 5){color_list[[i]] <- c(lighten(oc5,space = "combined",amount = 0.3),darken(oc5,space = "HCL",amount = 0.2))}
  if(coms[i,1] == 6){color_list[[i]] <- c(lighten(oc6,space = "combined",amount = 0.3),darken(oc6,space = "HCL",amount = 0.2))}
if(coms[i,1] == 7){color_list[[i]] <- c(lighten(oc7,space = "combined",amount = 0.3),darken(oc7,space = "HCL",amount = 0.2))}}
if(!is.na(pre_mgm$errors[i,2])){
  if(coms[i,1] == 1){color_list[[i]] <- darken(oc1,space = "HCL",amount = 0.2)}
  if(coms[i,1] == 2){color_list[[i]] <- darken(oc2,space = "HCL",amount = 0.2)}
  if(coms[i,1] == 3){color_list[[i]] <- darken(oc3,space = "HCL",amount = 0.2)}
  if(coms[i,1] == 4){color_list[[i]] <- darken(oc4,space = "HCL",amount = 0.2)}
  if(coms[i,1] == 5){color_list[[i]] <- darken(oc5,space = "HCL",amount = 0.2)}
  if(coms[i,1] == 6){color_list[[i]] <- darken(oc6,space = "HCL",amount = 0.2)}
  if(coms[i,1] == 7){color_list[[i]] <- darken(oc7,space = "HCL",amount = 0.2)}}  
}
```



```{r}
#pdf(file = "nw_plasma2.pdf")
nw_plot <- plot(nw, color = coms$color,pie = error_list,
pieColor = color_list, labels = "")
#dev.off()
```


Get adj matrix for supplements
```{r}
g_table <- as.data.frame(nw$graph)
g_table  <- g_table  %>% mutate_if(is.numeric, round, digits = 2)
g_table[g_table == 0] <- ""
g_table[upper.tri(g_table)] <- ""
g_table <- data.frame(Node = 1:30, g_table)
colnames(g_table) <- colnames(data_nw)
rownames(g_table) <- colnames(data_nw)
```





```{r}
#ft <- flextable(g_table)
#ft <- autofit(ft)                  
#ft <- set_table_properties(ft, layout = "autofit")  
#ft <- fontsize(ft, size = 6)
#doc <- read_docx() %>%             
# body_add_flextable(ft) %>%       
#  body_add_par("")                 


#doc <- read_docx() %>%
# body_add_flextable(ft) %>%
# body_end_section_landscape()

#print(doc, target = "output8.docx") # Save the Word document
```

 N1: "Perceived.Health";N2: "Social.Impact";              
 N3: "Dizziness";            N4:       "Fainting";                   
 N5: "Heart.Palpitations";   N6:       "Shortness.Of.Breath";        
 N7 "Anhedonia";            N8:       "Appetite.Dysregulation";     
 N9 "Psychomotor.Changes";  N10:       "Suicidal.Ideation";          
N11 "Panic.Attacks";        N12:       "Health.concerns";            
N13 "Trauma.Memories";      N14:       "Reduced.Talking";            
N15 "Perceived.Social.Rejection"; N16:  "Loss.of.drive";              
N17 "Pain.Impact";          N18:       "Libido.Loss";                
N19 "Loneliness";           N20:       "Self.Worth.Issues";          
N21 "Concentration.Deficits";  N22:    "Gastrointestinal.Discomfort";
N23 "Depressed.mood";       N24:       "Anxiety/Nervousness";        
N25 "Sleeping.Problems";    N26:       "Self.Efficacy";              
N27 "Pain.Severity";        N28:       "Pain.Distribution";          
N29 "Fatigue";              N30:       "Daily.Living.Skills" 




```{r}
nw_matrix <- nw$graph
colnames(nw_matrix) <- colnames(data_nw)
rownames(nw_matrix) <- colnames(data_nw)
nw_matrix
nw_matrix_only_pain <- as.data.frame(nw_matrix) %>% select(Pain.Severity) %>% filter(Pain.Severity != 0)
```

Export adj matrix
```{r}
network_df <- as.data.frame(nw$graph)
colnames(network_df) <- colnames(data_nw)

network_df2 <- network_df %>% mutate(aa = colnames(data_nw))
network_df2 <- network_df2 %>% select(aa, all_of(colnames(network_df2)))
colnames(network_df2)[1] <- "Node"


network_table <- nice_table(network_df2)
network_table
#print(network_table, preview = "docx")
```



Bootstrapping
Case
```{r}
#set.seed(777)
#boot_case <- bootnet(nw, nBoots = 5000,  type = "case", nCores = 7, 
#statistics = c("edge", "strength", "closeness", "betweenness", #"expectedInfluence","bridgeStrength","bridgeCloseness","bridgeBetweenness","bridgeExpectedInfluence"),
#communities = coms$x,
#useCommunities = "all")
#save(boot_case, file = "boot_case100924.Rda")
```

Nonparametric
```{r}
#set.seed(777)
#boot_np <- bootnet(nw, nBoots = 5000,  type = "nonparametric", nCores = 7, 
#statistics = c("edge", "strength", "expectedInfluence","bridgeStrength","bridgeCloseness","bridgeBetweenness","bridgeExpectedInfluence"),
#communities = coms$x,
#useCommunities = "all")
#save(boot_np, file = "boot_np100924.Rda")
```


```{r}
load("boot_np100924.Rda")
load("boot_case100924.Rda")
```

```{r}
corStability(boot_case)
```
Edge weight np
```{r}
#pdf(file = "boot_edges_nz_101024.pdf", width = 7,height = 60)
#plot(boot_np, labels = TRUE,order = "sample")
#dev.off()


#pdf(file = "boot_edges_010425.pdf", width = 7,height = 10)
#plot(boot_np, labels = FALSE,order = "sample")
#dev.off()
```

```{r}
#pdf(file = "strength_closeness_betweenness270225.pdf")
centralityPlot(nw, include = c("Strength","Closeness","Betweenness"), scale = "z-scores",orderBy = "default", decreasing = TRUE)
#dev.off()
```

z-scores
```{r}
ct_raw <- centralityTable(nw, standardized = FALSE)
ct_raw <- ct_raw %>% filter(measure == "Strength") %>% select(3,5) %>% rename(raw = value)
ct_raw$node <- colnames(data_nw)

ct_z <- centralityTable(nw, standardized = TRUE)
ct_z <- ct_z %>% filter(measure == "Strength") %>% select(3,5) %>% rename(z_score = value)
ct_z$node <- colnames(data_nw)

ct_man <- merge(ct_raw,ct_z, by = "node", all = TRUE)

```



```{r}
bridge <- networktools::bridge(nw$graph,communities = coms$x, normalize = FALSE)
names(bridge$`Bridge Strength`) <- colnames(data_nw)
```


```{r}
bridge_ct <- data.frame(node = colnames(data_nw),
                        raw = bridge$`Bridge Strength`
                        )

bridge_ct <- bridge_ct %>% mutate(z_score = (raw - mean(bridge_ct$raw)) / sd(raw))
```


```{r}
bridge$communities
all(coms$x == bridge$communities)
```


```{r}
#pdf(file = "bridge_plot270225.pdf")
bridge_plot <- plot(bridge,
order = "value",
zscore = TRUE,
color = FALSE,
#colpalette = "Set2",
plotNA = FALSE,
include = "Bridge Strength"
)
bridge_plot
#dev.off()
```

```{r}
#pdf(file = "bridge_plot270225.pdf")
#plot(bridge,
#order = "value",
#zscore = TRUE,
#color = FALSE,
#colpalette = "Set2",
#plotNA = FALSE,
#include = "Bridge Strength"
#)

#dev.off()
```

```{r}
b_zscores <- bridge$`Bridge Strength`
b_zscores <- (b_zscores- mean(b_zscores))/sd(b_zscores)
```



```{r}
#pdf(file = "bridge_closeness_betweenness270225.pdf")
plot(bridge,
#order = "value",
zscore = TRUE,
color = FALSE,
#colpalette = "Set2",
plotNA = FALSE,
include = c("Bridge Betweenness", "Bridge Closeness")
)

#dev.off()
```



```{r}
plot(boot_np,"BridgeStrength",plot = "difference",order = "mean")
```


Bridge edges for communities
```{r}
adj_matrix <- nw$graph
communities <- coms$x

all_coms <- c(1:7)
com_combination  <- as.data.frame(t(combn(all_coms,m = 2,simplify = TRUE)))
el <- rep("",30)
```

Create a bridge matrix
```{r}

adj_matrix_bridge <- adj_matrix  
for (i in 1:nrow(adj_matrix)) {
  for (j in 1:ncol(adj_matrix)) {
  #  browser()
    if (communities[i] == communities[j]) {  
 #    browser()
       adj_matrix_bridge[i, j] <- 0  # Set edge to 0 if nodes belong to the same community
 #      browser()
    }
  }
}
```

```{r}
#pdf(file = "bridges_nw_no_labels.pdf", width = 12, height = 9)
qgraph(adj_matrix_bridge, color = coms$color,pie = error_list,
pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = colnames(data_nw), minimum = 0) #maximum = max(adj_matrix)
#dev.off()
```



```{r}
#   pdf(file = "pain_com_bridge_figure270225.pdf", width = 12, height = 9)
#    qgraph(pain_matrix, color = coms$color,pie = error_list,
#    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,maximum = max(adj_matrix), directed = FALSE) #
#    dev.off()
```






Create a bridge matrix for each combination of communities. Only creates "half" of a matrix.So directed has to be FALSE. 
```{r}
create_adj_matrix <- function(adj_matrix, communities, community1, community2) {
  new_adj_matrix <- adj_matrix  
  for (i in 1:nrow(adj_matrix)) {
    for (j in 1:ncol(adj_matrix)) {
      if (communities[i] != community1 | communities[j] != community2) {  
        new_adj_matrix[i, j] <- 0  
      }
    }
  }
  return(new_adj_matrix)
}
```

```{r}
   # Initialize a list to store the adjacency matrices
adj_matrices <- list()

  # Iterate over each pair of communities and create adjacency matrix
for (i in 1:nrow(com_combination)){
    # Create adjacency matrix for current pair of communities
    community1 <- com_combination[i,1]
    community2 <- com_combination[i,2] 
    
    current_adj_matrix <- create_adj_matrix(adj_matrix, communities, community1, community2)
    
    # Store the adjacency matrix in the list
    adj_matrices[[length(adj_matrices) + 1]] <- current_adj_matrix
  
 
    }


```



Create a matrix only conataining bridge edges for the Pain Severity and Impact community
```{r}
pain_matrix <- adj_matrices[[1]] + adj_matrices[[2]] + adj_matrices[[3]] + adj_matrices[[4]] + adj_matrices[[5]] + adj_matrices[[6]]
pain_b <- as.vector(pain_matrix)
pain_b <- pain_b[pain_b != 0]
qgraph(pain_matrix, color = coms$color,pie = error_list,
    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,directed = FALSE)
```

```{r}
length(pain_b)
length(pain_b)/(26*4)
```


```{r}
sleep_matrix <- adj_matrices[[1]] + adj_matrices[[7]] + adj_matrices[[8]] + adj_matrices[[9]] + adj_matrices[[10]] + adj_matrices[[11]]
sleep_b <- as.vector(sleep_matrix)
sleep_b <- sleep_b[sleep_b != 0]
qgraph(sleep_matrix, color = coms$color,pie = error_list,
    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,directed = FALSE)
```

```{r}
length(sleep_b)
length(sleep_b)/(26*4)
```

```{r}
somatic_matrix <- adj_matrices[[2]] + adj_matrices[[7]] + adj_matrices[[12]] + adj_matrices[[13]] + adj_matrices[[14]] + adj_matrices[[15]] 
somatic_b <- as.vector(somatic_matrix)
somatic_b <- somatic_b[somatic_b != 0]
qgraph(somatic_matrix, color = coms$color,pie = error_list,
    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,directed = FALSE)
```

```{r}
length(somatic_b)
length(somatic_b)/(24*6)
```

```{r}
mood_matrix <- adj_matrices[[3]] + adj_matrices[[8]] + adj_matrices[[12]] + adj_matrices[[16]] + adj_matrices[[17]] + adj_matrices[[18]] 
mood_b <- as.vector(mood_matrix)
mood_b <- mood_b[mood_b != 0]
qgraph(mood_matrix, color = coms$color,pie = error_list,
    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,directed = FALSE)
```

```{r}
length(mood_b)
length(mood_b)/(24*6)
```
```{r}
cognitive_matrix <- adj_matrices[[4]] + adj_matrices[[9]] + adj_matrices[[13]] + adj_matrices[[16]] + adj_matrices[[19]] + adj_matrices[[20]] 
cognitive_b <- as.vector(cognitive_matrix)
cognitive_b <- cognitive_b[cognitive_b != 0]
qgraph(cognitive_matrix, color = coms$color,pie = error_list,
    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,directed = FALSE)
```

```{r}
length(cognitive_b)
length(cognitive_b)/(25*5)
```

```{r}
anxiety_matrix <- adj_matrices[[5]] + adj_matrices[[10]] + adj_matrices[[14]] + adj_matrices[[17]] + adj_matrices[[19]] + adj_matrices[[21]] 
anxiety_b <- as.vector(anxiety_matrix)
anxiety_b <- anxiety_b[anxiety_b != 0]
qgraph(anxiety_matrix, color = coms$color,pie = error_list,
    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,directed = FALSE)
```

```{r}
length(anxiety_b)
length(anxiety_b)/(27*3)
```

```{r}
sex_health_matrix <- adj_matrices[[6]] + adj_matrices[[11]] + adj_matrices[[15]] + adj_matrices[[18]] + adj_matrices[[20]] + adj_matrices[[21]] 
sex_health_b <- as.vector(sex_health_matrix)
sex_health_b <-sex_health_b[sex_health_b != 0]
qgraph(sex_health_matrix, color = coms$color,pie = error_list,
    pieColor = color_list, layout = nw_plot$layout,edge.color = "blue",labels = el,directed = FALSE)
```



```{r}
length(sex_health_b)
length(sex_health_b)/(28*2)
```












