---
title: "Cross Sectional Network Analysis"
author: "JR"
date: "03 04 2025"
output: html_document
---

Load packages
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(readxl)
library(ggplot2)
library(networktools)
library(car)
library(EGAnet)
library(lavaan)
```

Load data and recode sf12
```{r}
data_nwa_og <- read_excel("data_nwa.xlsx")
data_nwa <- read_excel("data_nwa.xlsx")
```

Delete Variables Step 1 
```{r}
data_nwa <- data_nwa %>% select(-c(1,3:38)) %>% # keep id col and delete all demographics values,medication and the four pain related question which were not part of the assessment between 2010 and 2012
                         select(-c(phq13,phq14,phq15)) %>% # Delete: Abuse, #Open ended, Medication
                         select(-c(starts_with("iip"))) %>% # Delete: IIP
                         select(-c(starts_with("fesv"))) %>% # Delete: FESV
                         select(-c(starts_with("index"))) %>%# Get rid of index variables
                         select(-c(ases9,ases10)) # Only NA values
```


Delete Variables Step 2
```{r}
data_nwa  <- data_nwa %>% select(-c(
  sf2:sf7, sf9, # SF12
  phq1d, #PHQ-som
  phq3b:phq4k,phq5b:phq10e, # PHQ- Diagnostic Modules
  phq12b,phq12d:phq12g,phq12i, # PHQ-stress
  fiq2:fiq4, # FIQ
  ads12)) #ADS
```

Get number of variables after step1 and step2
```{r}
ncol(data_nwa) - 1 # id col
```

Step 3 include variables:
Reverse score items so that for every variable higher scores indicated a more negative outcome
```{r}
data_nwa$sf12 <- car::recode(data_nwa$sf12,"1 = 5; 2 = 4; 3 = 3; 4 = 2; 5 = 1")
data_nwa$sf11 <- car::recode(data_nwa$sf11,"1 = 6; 2 = 5; 3 = 4; 4 = 3; 5 = 2; 6 = 1")
data_nwa$ads9 <- car::recode(data_nwa$ads9,"0 = 3; 1 = 2; 2 = 1; 3 = 0")

data_nwa$ases1 <- car::recode(data_nwa$ases1,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
data_nwa$ases2 <- car::recode(data_nwa$ases2,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
data_nwa$ases3 <- car::recode(data_nwa$ases3,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
data_nwa$ases4 <- car::recode(data_nwa$ases4,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
data_nwa$ases5 <- car::recode(data_nwa$ases5,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
data_nwa$ases6 <- car::recode(data_nwa$ases6,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
data_nwa$ases7 <- car::recode(data_nwa$ases7,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
data_nwa$ases8 <- car::recode(data_nwa$ases8,"1 = 10; 2 = 9; 3 = 8; 4 = 7; 5 = 6; 6 = 5; 7 = 4; 8 = 3; 9 = 2; 10 = 1")
```

Directly include symptom categories with only one item 
```{r}
items_include_1c <- c("sf1", # Perceived Health
                   "sf12", #Social Impact
                   "phq1h",# Dizziness
                   "phq1i",# Fainting
                   "phq1j",# Heart Racing
                   "phq1k",# Short Breath
                   "phq2a",# Anhedonia
                   "phq2e",# Appetite
                   "phq2h",# Activity Level
                   "phq2i", # Suicidal Ideation
                   "phq3a", # Panic Attacks
                   "phq12a", # Health Worry
                   "phq12j", # Trauma
                   "fiq8", # Morning Stiffness
                  "ads10", # Less Talk
                   "ads14", # Disliked
                   "ads15" # Motivation
                   
)
```


```{r}
summary(data_nwa$phq2g)
```

Select items for categories with 2 symptoms (see supplements)
Estimate new variable Gastrointestinal Discomfort
```{r}
items_include_2c <- c("sf8", # Pain Impact
                      "phq12c", # Libido Loss
                      "ads11", # Loneliness
                      "phq2f", # Self Esteem
                      "phq2g") # Concentration

# Create new gastro variable
table(data_nwa$phq1l) # Check whether data are correct
table(data_nwa$phq1m) # Check whether data are correct

gastro_data <- data_nwa %>% select(id,phq1l,phq1m) %>% 
                            drop_na() %>% 
                            mutate(gastro = phq1l + phq1m) %>%
                            select(id,gastro)

# Add to items include vector
items_include_2c <- c(items_include_2c,"gastro") # Gastrointestinal Discomfort new Variable
```


Items with 3 or more symptoms:


Pain
```{r}
pain_data <- data_nwa %>% select(id,phq1a,phq1b,phq1c,phq1f,phq1g,fiq5) %>% drop_na()

for (i in 2:7) {
  table_pain <- table(pain_data[,i])
  print(table_pain)
}
```

```{r}
ega_pain <- EGA(pain_data[,2:6]) # no id and no pain sev included
summary(ega_pain)
```

```{r}
pain_data$pain_sev <- pain_data$fiq5
pain_data <-  pain_data %>% mutate(pain_symptoms = phq1a + phq1b + phq1c + phq1f + phq1g) %>% select(id,pain_sev,pain_symptoms)

```


Depressed
```{r}
items_mood <- c("id",
                "sf11",
                "phq2b",
                "fiq10",
                "ads2",
                "ads4",
                "ads9",
                "ads13")

table(data_nwa$sf11) # Check whether data are correct
table(data_nwa$phq2b) # Check whether data are correct
table(data_nwa$fiq10) # Check whether data are correct
table(data_nwa$ads2) # Check whether data are correct
table(data_nwa$ads4) # Check whether data are correct
table(data_nwa$ads9) # Check whether data are correct
table(data_nwa$ads13) # Check whether data are correct

dep_cfa_data <- data_nwa %>% select(all_of(items_mood)) %>% drop_na() #DWLS does not allow missings
ega_dep <- EGA(dep_cfa_data[,2:8]) # Check for unidimensionality
summary(ega_dep)
```

EGA suggest unidimensionality

Perform Cfa for dep. mood items
```{r}
# Set fiq10 first because it has the best phrasing
model_dep <- 'dep =~  fiq10  + phq2b + ads2 + ads4 + ads9 + ads13 + sf11' 
fit_dep <- cfa(model_dep, data = dep_cfa_data, ordered = c("phq2b","ads2","ads4","ads13","ads9"))
summary(fit_dep,standardized = TRUE)
```

Get latent factor scores for depressed
```{r}
dep_scores <- lavPredict(fit_dep)
dep_cfa_data$depressed <- as.vector(dep_scores)
dep_cfa_data <- dep_cfa_data %>% select(id,depressed)
```


Anxious 
```{r}
items_anxious <- c("id",
                   "phq5a",
                   "fiq9",
                   "ads1",
                   "ads7")

table(data_nwa$phq5a) # Check whether data are correct
table(data_nwa$fiq9) # Check whether data are correct
table(data_nwa$ads1) # Check whether data are correct
table(data_nwa$ads7) # Check whether data are correct


anxious_cfa_data <- data_nwa %>% select(all_of(items_anxious)) %>% drop_na() #DWLS does not allow missings
ega_anxious <- EGA(anxious_cfa_data[,2:5]) # Check for unidimensionality
summary(ega_anxious)
```
EGA suggest unidimensionality

Perform cfa
```{r}
# Set phq5a first because it has the best phrasing
model_anxious <- 'anxious =~  phq5a + fiq9 + ads1 + ads7' 
fit_anxious <- cfa(model_anxious, data = anxious_cfa_data, ordered = c("phq5a","ads1","ads7"))
summary(fit_anxious,standardized = TRUE)
```

Get factor scores for anxious
```{r}
anxious_scores <- lavPredict(fit_anxious)
anxious_cfa_data$anxious <- as.vector(anxious_scores)
anxious_cfa_data <- anxious_cfa_data %>% select(id,anxious)
```


Sleep Quality
```{r}
items_sleep_quality <- c("id",
              "phq2c",
              "fiq7",
              "ads8")

table(data_nwa$phq2c) # Check whether data are correct
table(data_nwa$fiq7) # Check whether data are correct
table(data_nwa$ads8) # Check whether data are correct

sleep_quality_cfa_data <- data_nwa %>% select(all_of(items_sleep_quality)) %>% drop_na() #DWLS does not allow missings
ega_sleep_quality <- EGA(sleep_quality_cfa_data[,2:4]) #Check for unidimensionality
summary(ega_sleep_quality)
```

EGA suggest unidimensionality
```{r}
# Set phq2c first because it has the best phrasing
model_sleep_quality <- 'sleep_quality =~  phq2c + ads8 + fiq7' 
fit_sleep_quality <- cfa(model_sleep_quality, data = sleep_quality_cfa_data, ordered = c("phq2c","ads8"))
summary(fit_sleep_quality,standardized = TRUE)
```

```{r}
sleep_quality_scores <- lavPredict(fit_sleep_quality)
sleep_quality_cfa_data$sleep_quality <- as.vector(sleep_quality_scores)
sleep_quality_cfa_data <- sleep_quality_cfa_data %>% select(id,sleep_quality)
```



Fatigue
```{r}
items_fatigue <- c("id",
              "sf10",
              "phq2d",
              "fiq6",
              "ads5")

table(data_nwa$sf10) # Check whether data are correct
table(data_nwa$phq2d) # Check whether data are correct
table(data_nwa$fiq6) # Check whether data are correct
table(data_nwa$ads5) # Check whether data are correct


fatigue_cfa_data <- data_nwa %>% select(all_of(items_fatigue)) %>% drop_na() #DWLS does not allow missings
ega_fatigue <- EGA(fatigue_cfa_data[2:5]) #Check for unidimensionality
summary(ega_fatigue)
```


```{r}
# Set phq2c first because it has the best phrasing
model_fatigue <- 'fatigue =~  fiq6 + phq2d + ads5 + sf10' 
fit_fatigue <- cfa(model_fatigue, data = fatigue_cfa_data, ordered = c("phq2d","ads5"))
summary(fit_fatigue,standardized = TRUE)
```

```{r}
fatigue_scores <- lavPredict(fit_fatigue)
fatigue_cfa_data$fatigue <- as.vector(fatigue_scores)
fatigue_cfa_data <- fatigue_cfa_data %>% select(id,fatigue)
```


Self-efficacy 
```{r}
items_ases <- c("id",
                "ases1",
                "ases2",
                "ases3",
                "ases4",
                "ases5",
                "ases6",
                "ases7",
                "ases8"
              )

table(data_nwa$ases1) # Check whether data are correct
table(data_nwa$ases2) # Check whether data are correct
table(data_nwa$ases3) # Check whether data are correct
table(data_nwa$ases4) # Check whether data are correct
table(data_nwa$ases5) # Check whether data are correct
table(data_nwa$ases6) # Check whether data are correct
table(data_nwa$ases7) # Check whether data are correct
table(data_nwa$ases8) # Check whether data are correct
```
Some items are 0 and some are random numbers higher than 10 e.g. 62 or 21. Filter those cases out

```{r}
ases_data_control <- data_nwa %>% select(all_of(items_ases)) %>% drop_na()  #DWLS does not allow missings
                                                        
table(ases_data_control$ases1) # Check whether data are correct
table(ases_data_control$ases2) # Check whether data are correct
table(ases_data_control$ases3) # Check whether data are correct
table(ases_data_control$ases4) # Check whether data are correct
table(ases_data_control$ases5) # Check whether data are correct
table(ases_data_control$ases6) # Check whether data are correct
table(ases_data_control$ases7) # Check whether data are correct
table(ases_data_control$ases8) # Check whether data are correct

nrow(ases_data_control)
```


```{r}
ases_data_control2 <- data_nwa %>% select(all_of(items_ases)) %>% drop_na() %>%  #DWLS does not allow missings
                                                          #DWLS does not allow missings
                                                         filter(ases1 > 10 | ases1 < 1 |                                                                                                          ases2 > 10 |   ases2 < 1 |
                                                               ases3 > 10 |   ases3 < 1 |
                                                               ases4 > 10 |   ases4 < 1 |
                                                               ases5 > 10 |   ases5 < 1 |
                                                               ases6 > 10 |   ases6 < 1 |
                                                               ases7 > 10 |   ases7 < 1 |
                                                                ases8 > 10 |   ases8 < 1)
nrow(ases_data_control2)
```

Now everything is right
```{r}
ases_cfa_data <- data_nwa %>% select(all_of(items_ases)) %>% drop_na() %>%  
                                                      
                                                         filter(ases1 <= 10 &   ases1  >= 1,                                                                                                      ases2 <= 10 &   ases2 >= 1, 
                                                                ases3 <= 10 &   ases3 >= 1,
                                                                ases4 <= 10 &   ases4 >= 1,
                                                                ases5 <= 10 &   ases5 >= 1,
                                                                ases6 <= 10 &   ases6 >= 1,
                                                                ases7 <= 10 &   ases7 >= 1,
                                                                ases8 <= 10 &   ases8 >= 1)
nrow(ases_cfa_data)
```

```{r}
ega_ases <- EGA(ases_cfa_data[2:9])
summary(ega_ases)
```



```{r}
ases_cfa_data <- ases_cfa_data %>% mutate(self_e = (ases1 + ases2 + ases3 + ases4 + ases5 + ases6 + ases7 + ases8)/8) %>%
select(id,self_e)
```


Daily living skills
```{r}
fi_d <- data_nwa %>% select(id,fiq1a:fiq1j,ffbh1:ffbh18) 
for (i in 2:ncol(fi_d)) {
  table_result <-table(fi_d[,i])
  print(table_result)
  }
```

Some fiq1 items have wrong numbers (higher than 3). We filter these out.
```{r}
fi_control <- data_nwa %>% select(id,fiq1a:fiq1j) %>% filter(
                                                     fiq1a >= 4 |
                                                     fiq1b >= 4 | 
                                                     fiq1c >= 4 | 
                                                     fiq1d >= 4 | 
                                                     fiq1e >= 4 | 
                                                     fiq1f >= 4 | 
                                                     fiq1g >= 4 | 
                                                     fiq1h >= 4 | 
                                                     fiq1i >= 4 | 
                                                     fiq1j >= 4)
```

23



Functional impairment
```{r}
fi_data <- data_nwa %>% select(id,fiq1a:fiq1j,ffbh1:ffbh18) %>% filter(
                                                     fiq1a < 4 | is.na(fiq1a),
                                                     fiq1b < 4 | is.na(fiq1b),
                                                     fiq1c < 4 | is.na(fiq1c),
                                                     fiq1d < 4 | is.na(fiq1d),
                                                     fiq1e < 4 | is.na(fiq1e),
                                                     fiq1f < 4 | is.na(fiq1f),
                                                     fiq1g < 4 | is.na(fiq1g),
                                                     fiq1h < 4 | is.na(fiq1h),
                                                     fiq1i < 4 | is.na(fiq1i),
                                                     fiq1j < 4 | is.na(fiq1j))

fi_data$fiq_sum <- rowMeans(fi_data[,2:11],na.rm = TRUE)
```


```{r}
fi_data <- fi_data %>% select(-c(2:11)) # drop single fiq items
```


```{r}
ega_fi <- EGA(fi_data[2:20])
summary(ega_fi)
```


```{r}
hands_cfa_data <- fi_data %>% select(id,ffbh1,ffbh3,ffbh4) %>% drop_na() %>% mutate(hands = (ffbh1 + ffbh3 + ffbh4)) %>% select(id,hands)
                                  #DWLS does not allow missings
```

```{r}
#model_hands <- 'hands =~   ffbh3 + ffbh1 + ffbh4' 
#fit_hands <- cfa(model_hands, data = hands_cfa_data, ordered = c("ffbh3","ffbh1","ffbh4"))
#summary(fit_hands,standardized = TRUE)
```

```{r}
#hands_scores <- lavPredict(fit_hands)
#hands_cfa_data$hands <- as.vector(hands_scores)
#hands_cfa_data <- hands_cfa_data %>% select(id,hands)
```


```{r}
physical_cfa_data <- fi_data %>% select(id,fiq_sum,ffbh6,ffbh10,ffbh11,ffbh15,ffbh17) %>% drop_na() #DWLS does not allow missings
```

```{r}
model_physical <- 'physical =~   fiq_sum + ffbh6 + ffbh10 + ffbh11 + ffbh15 + ffbh17' 
fit_physical <- cfa(model_physical, data = physical_cfa_data, ordered = c("ffbh6","ffbh10","ffbh11","ffbh15","ffbh17"))
summary(fit_physical,standardized = TRUE)
```

```{r}
physical_scores <- lavPredict(fit_physical)
physical_cfa_data$physical <- as.vector(physical_scores)
physical_cfa_data <- physical_cfa_data %>% select(id,physical)
```


```{r}
move_cfa_data <- fi_data %>% select(id,ffbh2,ffbh5,ffbh7,ffbh8,ffbh9,ffbh12,ffbh13,ffbh14,ffbh16,ffbh18) %>% drop_na() %>% 
                             mutate(move = (ffbh2 + ffbh5 + ffbh7 + ffbh8 + ffbh9 + ffbh12 +ffbh13 + ffbh14 + ffbh16 + ffbh18)) %>% select(id,move)
```


```{r}
items_include_3c <- c("depressed","anxious","sleep_quality","self_e","hands","physical","move","pain_sev",
                      "pain_symptoms","fatigue")
```


```{r}
data_final <- merge(data_nwa,gastro_data, by = "id", all = TRUE)
data_final <- merge(data_final,dep_cfa_data, by = "id", all = TRUE)
data_final <- merge(data_final,anxious_cfa_data, by = "id", all = TRUE)
data_final <- merge(data_final,sleep_quality_cfa_data, by = "id", all = TRUE)
data_final <- merge(data_final,ases_cfa_data, by = "id", all = TRUE)
data_final <- merge(data_final,hands_cfa_data, by = "id", all = TRUE)
data_final <- merge(data_final,physical_cfa_data, by = "id", all = TRUE)
data_final <- merge(data_final,move_cfa_data, by = "id", all = TRUE)
data_final <- merge(data_final,pain_data, by = "id", all = TRUE)
data_final <- merge(data_final,fatigue_cfa_data, by = "id", all = TRUE)
```


```{r}
#save(data_final, file = "data_final1105.Rda")
load("data_final1105.Rda")
```


```{r}
vars_final <- c(items_include_1c,items_include_2c,items_include_3c)
#save(vars_final, file = "vars_final1105.Rda")
#load("vars_final1105.Rda")
```

```{r}
data_uva <- data_final %>% select(all_of(vars_final)) %>% drop_na()
```


```{r}
data_cor <- cor(data_uva, method = "spearman")
```

```{r}
UVA(data_cor, n = 3059)
```

```{r}
cor(data_uva$anxious,data_uva$phq3a)
```

```{r}
goldbricker(data_uva, corMin = .5)
```



```{r}
uva_t <- UVA(data_cor, n = 3059)
uva_t2 <- uva_t$wto$pairwise
uva_t2 <- uva_t2 %>% filter(wto >= .25)

uva_t2$node_i <- car::recode(uva_t2$node_i, "'fiq8' = 'Stiffness';
                                             'pain_sev' = 'Pain Severity';
                                             'physical' = 'Physical Ability';
                                             'hands' = 'Hands functioning';
                                             'move' = 'Ability to move';
                                             'phq3a' = 'Panic Attacks';
                                             'phq1j' = 'Heart Racing';
                                             'phq1k' = 'Short Breath';
                                             'anxious' = 'Anxious'")


uva_t2$node_j <- car::recode(uva_t2$node_j, "'fiq8' = 'Stiffness';
                                             'pain_sev' = 'Pain Severity';
                                             'physical' = 'Physical Ability';
                                             'hands' = 'Hands functioning';
                                             'move' = 'Ability to move';
                                             'phq3a' = 'Panic Attacks';
                                             'phq1j' = 'Heart Racing';
                                             'phq1k' = 'Short Breath';
                                             'anxious' = 'Anxious'")
```

```{r}
library(rempsyc)
```

```{r}
wto_table <- nice_table(uva_t2, title = "Table SX", note = c("Result of the unique variable analysis for node pairs with Wto scores >= .25"))
```

```{r}
print(wto_table, preview = "docx")
```


```{r}
#library("writexl")
#write_xlsx(uva_t2, "wto_scores0505.xlsx")
```

Functional impairment
```{r}
imp_new <- data_final %>% select(id,fiq1a:fiq1j,ffbh1:ffbh18) %>% filter(
                                                     fiq1a < 4 | is.na(fiq1a),
                                                     fiq1b < 4 | is.na(fiq1b),
                                                     fiq1c < 4 | is.na(fiq1c),
                                                     fiq1d < 4 | is.na(fiq1d),
                                                     fiq1e < 4 | is.na(fiq1e),
                                                     fiq1f < 4 | is.na(fiq1f),
                                                     fiq1g < 4 | is.na(fiq1g),
                                                     fiq1h < 4 | is.na(fiq1h),
                                                     fiq1i < 4 | is.na(fiq1i),
                                                     fiq1j < 4 | is.na(fiq1j))

imp_new$fiq_mean <- rowMeans(imp_new[,2:11],na.rm = TRUE)
imp_new <- imp_new %>% select(id,fiq_mean,ffbh1:ffbh18) %>% drop_na()
```

```{r}
# Set phq2c first because it has the best phrasing
model_physical_imp <- 'hands =~   ffbh3 + ffbh1 + ffbh4
                       move =~   ffbh2 + ffbh5 + ffbh7 + ffbh8 + ffbh9 + ffbh12 + ffbh13 + ffbh14 + ffbh16 +ffbh18
                       physical =~   fiq_mean + ffbh6 + ffbh10 + ffbh11 + ffbh15 + ffbh17
                       physical_imp =~ physical + move + hands' 
fit_physical_imp <- cfa(model_physical_imp, data = imp_new, ordered = c("ffbh1","ffbh2","ffbh3","ffbh4","ffbh5","ffbh6",
                                                                 "ffbh7","ffbh8","ffbh9","ffbh10","ffbh11","ffbh12",                                                                 "ffbh13","ffbh14","ffbh15","ffbh16","ffbh17","ffbh18"))
summary(fit_physical_imp,standardized = TRUE)
```

```{r}
physical_imp_scores <- lavPredict(fit_physical_imp)
imp_new$physical_imp <- as.vector(physical_imp_scores[,4,drop = TRUE])
imp_new <- imp_new %>% select(id,physical_imp)
```

```{r}
data_final2 <- merge(data_final,imp_new, by = "id", all = TRUE)
```



```{r}
vars_final2 <- c(vars_final,"physical_imp")
vars_exclude <- c(which(vars_final2 == "fiq8"),
which(vars_final2 == "hands"),
which(vars_final2 == "move"),
which(vars_final2 == "physical"))
vars_final2 <- vars_final2[-c(vars_exclude)]
```




```{r}
save(data_final2, file = "data_final2_100924.Rda")

```


```{r}
#vars_final <- c(items_include_1c,items_include_2c,items_include_3c)
save(vars_final2, file = "vars_final2_100924.Rda")

```













